---
title: "Studies 1-3: Bucket analyses"
output: 
  html_notebook:
    toc: true
    toc_float: true
---

This is a notebook delving into the "bucket"-style, alternative analyses for Studies 1-3. In this analysis, we define three categories, or "buckets," of mental capacities—_BODY_ capacites, _HEART_ capacities, and _MIND_ capacities. To do this, we take the six items with the strongest positive factor loadings on each of these factors, according to an EFA of adults' responses. We chose six items per "bucket" in order to have an even number of items in each category.

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67, 
                      include = F, echo = F)
```

```{r}
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}
```

```{r}
# RUN DIMKID_MANUSCRIPT.RMD FIRST!
```

# Study 1

## Define buckets

```{r}
d1_buckets <- loadings_fun(efa_3_d1_ad) %>%
  mutate(factor = recode_factor(factor,
                                "F2" = "BODY",
                                "F1" = "HEART",
                                "F3" = "MIND")) %>%
  group_by(factor) %>%
  top_n(6, loading) %>%
  ungroup()
```

```{r}
d1_all_endorse <- d1_buckets %>%
  select(-loading) %>%
  left_join(d1_all) %>%
  mutate(endorse = ifelse(response_num > 0, 1, 0)) %>%
  group_by(age_group, subid, character, factor) %>%
  summarise(n = length(endorse),
            sum_endorse = sum(endorse, na.rm = T),
            prop_endorse = mean(endorse, na.rm = T)) %>%
  ungroup()
```

## Scatter

Let's look at the proportion of participants in each age group whose endorsements "match" across buckets - I'll count endorsement scores <3 as low, >=3 as high, and "matches" as two "low" scores or two "high" scores. We'd predict that, for distinctions that increase over development, there would be _fewer_ adults that "match" than children.

```{r, include = T}
d1_all_match_tab <- d1_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  mutate_at(vars(BODY, HEART, MIND),
            funs(ifelse(. < 3, "less than 3", "3 or more"))) %>%
  mutate(BODY_HEART_match = (BODY == HEART),
         BODY_MIND_match = (BODY == MIND),
         HEART_MIND_match = (HEART == MIND)) %>%
  select(-c(BODY, HEART, MIND)) %>%
  gather(pair, match, ends_with("_match")) %>%
  count(age_group, pair, match) %>%
  group_by(age_group, pair) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup() %>%
  filter(match == TRUE) %>%
  select(age_group, pair, prop) %>%
  arrange(pair, age_group) %>%
  mutate(pair = gsub("_match", "", pair))
d1_all_match_tab
```

```{r, include = T}
d1_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  ggplot(aes(x = BODY, y = HEART, color = age_group)) +
  geom_hline(yintercept = 3, lty = 2) +
  geom_vline(xintercept = 3, lty = 2) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0.2) +
  geom_smooth(aes(group = age_group), method = "lm")

d1_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  ggplot(aes(x = BODY, y = MIND, color = age_group)) +
  geom_hline(yintercept = 3, lty = 2) +
  geom_vline(xintercept = 3, lty = 2) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0.2) +
  geom_smooth(aes(group = age_group), method = "lm")

d1_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  ggplot(aes(x = HEART, y = MIND, color = age_group)) +
  geom_hline(yintercept = 3, lty = 2) +
  geom_vline(xintercept = 3, lty = 2) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0.2) +
  geom_smooth(aes(group = age_group), method = "lm")
```

```{r}
temp <- d1_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  mutate_at(vars(BODY, HEART, MIND),
            funs(ifelse(. < 3, "less than 3", "3 or more"))) %>%
  mutate(BODY_HEART_match = (BODY == HEART),
         BODY_MIND_match = (BODY == MIND),
         HEART_MIND_match = (HEART == MIND)) %>%
  select(-c(BODY, HEART, MIND)) %>%
  gather(pair, match, ends_with("_match")) %>%
  mutate(character = factor(character),
         pair = factor(pair))

contrasts(temp$age_group) <- cbind("79_ad" = c(1, 0))
contrasts(temp$character) <- cbind("R_GM" = c(-1, 1))
contrasts(temp$pair) <- cbind("BH_GM" = c(1, -1, 0),
                              "HM_GM" = c(0, -1, 1))

r_temp <- glm(match ~ age_group * character * pair, 
              data = temp,
              family = "binomial")

summary(r_temp)
```


## Examine first-order age trends

```{r, include = T}
ggplot(d1_all_endorse, 
       aes(x = prop_endorse, color = age_group, fill = age_group)) +
  facet_grid(character ~ factor) +
  geom_histogram(position = "identity", binwidth = 1/6, alpha = 0.5) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = seq(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r}
d1_all_endorse_boot <- d1_all_endorse %>%
  group_by(age_group, character, factor) %>%
  multi_boot_standard(col = "prop_endorse") %>%
  ungroup()
```

```{r}
figSUPP1_plot <- d1_all_endorse %>%
  filter(age_group != "adults") %>%
  left_join(d1_79 %>% distinct(subid, age)) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = prop_endorse, 
             fill = character, color = character, shape = character)) +
  facet_wrap(~ factor) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.03) +
  binomial_smooth(aes(weight = n), show.legend = F) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d1_all_endorse %>% filter(age_group == "adults"),
             aes(x = 11), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.03,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d1_all_endorse_boot %>% filter(age_group == "adults"),
                  aes(x = 11, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(7:11), 
                     labels = c(paste0(7:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = 0:6) +
  scale_color_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_fill_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_shape_manual(values = c(21, 22)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "number of items endorsed (out of 6)")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP1_with_caption <- add_sub(figSUPP1_plot, str_wrap("Figure SUPP1: Number of mental capacity items (out of 6) endorsed in each domain (BODY, HEART, and MIND) by 7- to 9-year-old children and adults in Study 1, in which each participant assessed 40 mental capacities for one of two target characters: a beetle (pink circles) or a robot (blue squares). We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP1_with_caption)
```

## Examine difference scores

```{r}
d1_all_endorse_diff <- d1_all_endorse %>%
  select(age_group, subid, character, factor, prop_endorse) %>%
  spread(factor, prop_endorse) %>%
  group_by(age_group, subid, character) %>%
  mutate(`BODY minus HEART` = BODY - HEART,
         `BODY minus MIND` = BODY - MIND,
         `MIND minus HEART` = MIND - HEART) %>%
  ungroup() %>% 
  select(-c(BODY, HEART, MIND)) %>%
  gather(comparison, difference, contains("min")) %>%
  mutate(diff_01 = (difference + 1)/2,
         diff_01_abs = abs(difference),
         character = factor(character),
         comparison = factor(comparison))
```

```{r, include = T}
ggplot(d1_all_endorse_diff, 
       aes(x = diff_01, color = age_group, fill = age_group)) +
  facet_grid(character ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/12, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r, include = T}
ggplot(d1_all_endorse_diff, 
       aes(x = diff_01, color = age_group, fill = age_group)) +
  facet_grid(. ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/12, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r}
d1_all_endorse_diff_boot <- d1_all_endorse_diff %>%
  group_by(age_group, character, comparison) %>%
  multi_boot_standard(col = "diff_01") %>%
  ungroup()
```

```{r}
figSUPP2_plot <- d1_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d1_79 %>% distinct(subid, age)) %>%
  filter(!is.na(age)) %>%
  mutate(y = (difference + 6)/12) %>%
  ggplot(aes(x = age, y = diff_01, 
             fill = character, color = character, shape = character)) +
  facet_wrap(~ comparison) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d1_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 11), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d1_all_endorse_diff_boot %>% filter(age_group == "adults"),
                  aes(x = 11, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(7:11), 
                     labels = c(paste0(7:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/12), labels = seq(-6, 6, 1)) +
  scale_color_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_fill_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_shape_manual(values = c(21, 22)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "differences in number of items endorsed (out of 6)")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP2_with_caption <- add_sub(figSUPP2_plot, str_wrap("Figure SUPP2: Differences in the number of mental capacity items (out of 6) endorsed across the three domains (BODY minus HEART, BODY minus MIND, and MIND minus HEART) by 7- to 9-year-old children and adults in Study 1, in which each participant assessed 40 mental capacities for one of two target characters: a beetle (pink circles) or a robot (blue squares). We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP2_with_caption)
```

## Examine absolute difference scores

```{r}
d1_all_endorse_diff_abs_boot <- d1_all_endorse_diff %>%
  group_by(age_group, character, comparison) %>%
  multi_boot_standard(col = "diff_01_abs") %>%
  ungroup()
```

```{r, include = T}
ggplot(d1_all_endorse_diff, 
       aes(x = diff_01_abs, color = age_group, fill = age_group)) +
  facet_grid(character ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/6, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r, include = T}
ggplot(d1_all_endorse_diff, 
       aes(x = diff_01_abs, color = age_group, fill = age_group)) +
  facet_grid(. ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/6, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r}
contrasts(d1_all_endorse_diff$age_group) <- cbind("79_ad" = c(1, 0))
contrasts(d1_all_endorse_diff$character) <- cbind("r_GM" = c(-1, 1))
contrasts(d1_all_endorse_diff$comparison) <- cbind("BH_GM" = c(1, -1, 0),
                                                   "MH_GM" = c(0, -1, 1))

# rs1_bucket_gp <- brm(diff_01_abs ~ age_group * character * comparison + (1|subid),
#                      data = d1_all_endorse_diff %>%
#                        mutate(diff_01_abs = case_when(
#                          diff_01_abs == 0 ~ diff_01_abs + 0.00000001,
#                          diff_01_abs == 1 ~ diff_01_abs - 0.00000001)),
#                      family = "Beta")
summary(rs1_bucket_gp)

fixef(rs1_bucket_gp) %>% round(2) %>%
  data.frame() %>%
  rownames_to_column("param") %>%
  mutate("nonzero" = ifelse(Q2.5 * Q97.5 > 0, "*", "")) %>%
  select(param, Estimate, nonzero)
```


```{r}
figSUPP3_plot <- d1_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d1_79 %>% distinct(subid, age)) %>%
  filter(!is.na(age)) %>%
  mutate(y = (difference + 6)/12) %>%
  ggplot(aes(x = age, y = diff_01_abs, 
             fill = character, color = character, shape = character)) +
  facet_wrap(~ comparison) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d1_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 11), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d1_all_endorse_diff_abs_boot %>% 
                    filter(age_group == "adults"),
                  aes(x = 11, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(7:11), 
                     labels = c(paste0(7:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = seq(0, 6, 1)) +
  scale_color_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_fill_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_shape_manual(values = c(21, 22)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "asbolute differences in number of items endorsed (out of 6)")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP3_with_caption <- add_sub(figSUPP3_plot, str_wrap("Figure SUPP2: Absolute differences in the number of mental capacity items (out of 6) endorsed across the three domains (BODY minus HEART, BODY minus MIND, and MIND minus HEART) by 7- to 9-year-old children and adults in Study 1, in which each participant assessed 40 mental capacities for one of two target characters: a beetle (pink circles) or a robot (blue squares). We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP3_with_caption)
```


# Study 2

## Define buckets

```{r}
d2_buckets <- loadings_fun(efa_3_d2_ad) %>%
  mutate(factor = recode_factor(factor,
                                "F1" = "BODY",
                                "F2" = "HEART",
                                "F3" = "MIND")) %>%
  group_by(factor) %>%
  top_n(6, loading) %>%
  ungroup()
```

```{r}
d2_all_endorse <- d2_buckets %>%
  select(-loading) %>%
  left_join(d2_all) %>%
  mutate(endorse = ifelse(response_num > 0, 1, 0)) %>%
  left_join(d2_anim %>% distinct(character, anim_inan)) %>%
  group_by(age_group, subid, anim_inan, character, factor) %>%
  summarise(n = length(endorse),
            sum_endorse = sum(endorse, na.rm = T),
            prop_endorse = mean(endorse, na.rm = T)) %>%
  ungroup()
```

## Scatter

Let's look at the proportion of participants in each age group whose endorsements "match" across buckets - I'll count endorsement scores <3 as low, >=3 as high, and "matches" as two "low" scores or two "high" scores. We'd predict that, for distinctions that increase over development, there would be _fewer_ adults that "match" than children.

```{r, include = T}
d2_all_match_tab <- d2_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  mutate_at(vars(BODY, HEART, MIND),
            funs(ifelse(. < 3, "less than 3", "3 or more"))) %>%
  mutate(BODY_HEART_match = (BODY == HEART),
         BODY_MIND_match = (BODY == MIND),
         HEART_MIND_match = (HEART == MIND)) %>%
  select(-c(BODY, HEART, MIND)) %>%
  gather(pair, match, ends_with("_match")) %>%
  count(age_group, pair, match) %>%
  group_by(age_group, pair) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup() %>%
  filter(match == TRUE) %>%
  select(age_group, pair, prop) %>%
  arrange(pair, age_group) %>%
  mutate(pair = gsub("_match", "", pair))
d2_all_match_tab
```

```{r, include = T}
d2_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  ggplot(aes(x = BODY, y = HEART, color = age_group)) +
  geom_hline(yintercept = 3, lty = 2) +
  geom_vline(xintercept = 3, lty = 2) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0.2) # +
  # geom_smooth(aes(group = age_group), method = "lm")

d2_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  ggplot(aes(x = BODY, y = MIND, color = age_group)) +
  geom_hline(yintercept = 3, lty = 2) +
  geom_vline(xintercept = 3, lty = 2) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0.2) # +
  # geom_smooth(aes(group = age_group), method = "lm")

d2_all_endorse %>%
  select(age_group, subid, character, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  ggplot(aes(x = HEART, y = MIND, color = age_group)) +
  geom_hline(yintercept = 3, lty = 2) +
  geom_vline(xintercept = 3, lty = 2) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0.2) # +
  # geom_smooth(aes(group = age_group), method = "lm")
```

```{r}
temp <- d2_all_endorse %>%
  select(age_group, subid, anim_inan, factor, sum_endorse) %>%
  spread(factor, sum_endorse) %>%
  mutate_at(vars(BODY, HEART, MIND),
            funs(ifelse(. < 3, "less than 3", "3 or more"))) %>%
  mutate(BODY_HEART_match = (BODY == HEART),
         BODY_MIND_match = (BODY == MIND),
         HEART_MIND_match = (HEART == MIND)) %>%
  select(-c(BODY, HEART, MIND)) %>%
  gather(pair, match, ends_with("_match")) %>%
  mutate(anim_inan = factor(anim_inan),
         pair = factor(pair)) %>%
  left_join(d2_46 %>% distinct(subid, age) %>%
              full_join(d2_79 %>% distinct(subid, age)))

contrasts(temp$age_group) <- cbind("79_ad" = c(0, 1, 0),
                                   "46_ad" = c(1, 0, 0))
contrasts(temp$pair) <- cbind("BH_GM" = c(1, -1, 0),
                              "HM_GM" = c(0, -1, 1))
contrasts(temp$anim_inan) <- cbind("anim_GM" = c(-1, 1))

temp_anim <- temp %>% filter(anim_inan == "animate")
temp_inan <- temp %>% filter(anim_inan == "inanimate")

r_temp_exact <- glm(match ~ age * pair * anim_inan,
                    data = temp %>%
                      filter(!is.na(age)) %>%
                      mutate(age = scale(age, scale = F)),
                    family = "binomial")

summary(r_temp_exact)

r_temp_group_anim <- glm(match ~ age_group * pair,
                         data = temp_anim,
                         family = "binomial")

summary(r_temp_group_anim)

r_temp_group_inan <- glm(match ~ age_group * pair,
                         data = temp_inan,
                         family = "binomial")

summary(r_temp_group_inan)
```

```{r}
temp %>%
  distinct() %>%
  ggplot(aes(x = age_group, fill = match)) +
  facet_grid(anim_inan ~ pair) +
  geom_bar(position = "fill")
```


## Examine first-order age trends

```{r}
d2_all_endorse_boot_anim <- d2_all_endorse %>%
  group_by(age_group, anim_inan, factor) %>%
  multi_boot_standard(col = "prop_endorse") %>%
  ungroup()
```

```{r, include = T}
ggplot(d2_all_endorse, 
       aes(x = prop_endorse, color = age_group, fill = age_group)) +
  facet_grid(anim_inan ~ factor) +
  geom_histogram(position = "identity", binwidth = 1/6, alpha = 0.5) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r}
figSUPP4a_plot <- d2_all_endorse %>%
  filter(age_group != "adults") %>%
  left_join(d2_79 %>% distinct(subid, age) %>%
              full_join(d2_46 %>% distinct(subid, age))) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = prop_endorse, 
             fill = anim_inan, color = anim_inan)) +
  facet_wrap(~ factor) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.03) +
  binomial_smooth(aes(weight = n), show.legend = F, alpha = 0.05) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d2_all_endorse %>% filter(age_group == "adults"),
             aes(x = 12), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.03,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d2_all_endorse_boot_anim %>% filter(age_group == "adults"),
                  aes(x = 12, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:10, 12), 
                     labels = c(paste0(4:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = 0:6) +
  scale_color_manual(values = c("slategrey", "firebrick1"), na.value = "gray") +
  scale_fill_manual(values = c("slategrey", "firebrick1"), na.value = "gray") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "number of items endorsed (out of 6)")
```

```{r}
d2_all_endorse_boot <- d2_all_endorse %>%
  group_by(age_group, character, factor) %>%
  multi_boot_standard(col = "prop_endorse") %>%
  ungroup()
```

```{r}
figSUPP4b_plot <- d2_all_endorse %>%
  filter(age_group != "adults") %>%
  left_join(d2_79 %>% distinct(subid, age) %>%
              full_join(d2_46 %>% distinct(subid, age))) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = prop_endorse, 
             fill = character, color = character)) +
  facet_wrap(~ factor) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.03) +
  binomial_smooth(aes(weight = n), show.legend = F, alpha = 0.05) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d2_all_endorse %>% filter(age_group == "adults"),
             aes(x = 12), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.03,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d2_all_endorse_boot %>% filter(age_group == "adults"),
                  aes(x = 12, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:10, 12), 
                     labels = c(paste0(4:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = 0:6) +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "number of items endorsed (out of 6)")
```

```{r}
figSUPP4_plots <- plot_grid(figSUPP4a_plot, figSUPP4b_plot, 
                            ncol = 1, labels = "AUTO")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP4_with_caption <- add_sub(figSUPP4_plots, str_wrap("Figure SUPP4: Number of mental capacity items (out of 6) endorsed in each domain (BODY, HEART, and MIND) by 4- to 9-year-old children and adults in Study 2, in which each participant assessed 20 mental capacities for one of nine target characters. We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 132), x = 0, hjust = 0)
ggdraw(figSUPP4_with_caption)
```

## Examine difference scores

```{r}
d2_all_endorse_diff <- d2_all_endorse %>%
  select(age_group, subid, character, factor, prop_endorse) %>%
  left_join(d2_anim %>% distinct(character, anim_inan)) %>%
  spread(factor, prop_endorse) %>%
  group_by(age_group, subid, character) %>%
  mutate(`BODY minus HEART` = BODY - HEART,
         `BODY minus MIND` = BODY - MIND,
         `MIND minus HEART` = MIND - HEART) %>%
  ungroup() %>% 
  select(-c(BODY, HEART, MIND)) %>%
  gather(comparison, difference, contains("min")) %>%
  mutate(diff_01 = (difference + 1)/2,
         diff_01_abs = abs(difference))
```

```{r, include = T}
ggplot(d2_all_endorse_diff, 
       aes(x = diff_01, color = age_group, fill = age_group)) +
  facet_grid(anim_inan ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/12, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r, include = T}
ggplot(d2_all_endorse_diff, 
       aes(x = diff_01, color = age_group, fill = age_group)) +
  facet_grid(. ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/12, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r}
d2_all_endorse_diff_boot_anim <- d2_all_endorse_diff %>%
  group_by(age_group, anim_inan, comparison) %>%
  multi_boot_standard(col = "diff_01") %>%
  ungroup()
```

```{r}
figSUPP5a_plot <- d2_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d2_79 %>% distinct(subid, age) %>%
              full_join(d2_46 %>% distinct(subid, age))) %>%
  filter(!is.na(age)) %>%
  mutate(y = (difference + 6)/12) %>%
  ggplot(aes(x = age, y = diff_01, 
             fill = anim_inan, color = anim_inan)) +
  facet_wrap(~ comparison) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F, alpha = 0.05) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d2_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 12), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d2_all_endorse_diff_boot_anim %>% 
                    filter(age_group == "adults"),
                  aes(x = 12, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:10, 12), 
                     labels = c(paste0(4:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/12), labels = seq(-6, 6, 1)) +
  scale_color_manual(values = c("slategrey", "firebrick1"), na.value = "gray") +
  scale_fill_manual(values = c("slategrey", "firebrick1"), na.value = "gray") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "differences in number of items endorsed (out of 6)")
```

```{r}
d2_all_endorse_diff_boot <- d2_all_endorse_diff %>%
  group_by(age_group, character, comparison) %>%
  multi_boot_standard(col = "diff_01") %>%
  ungroup()
```

```{r}
figSUPP5b_plot <- d2_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d2_79 %>% distinct(subid, age) %>%
              full_join(d2_46 %>% distinct(subid, age))) %>%
  filter(!is.na(age)) %>%
  mutate(y = (difference + 6)/12) %>%
  ggplot(aes(x = age, y = diff_01, 
             fill = character, color = character)) +
  facet_wrap(~ comparison) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F, alpha = 0.05) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d2_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 12), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d2_all_endorse_diff_boot %>% filter(age_group == "adults"),
                  aes(x = 12, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:10, 12), 
                     labels = c(paste0(4:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/12), labels = seq(-6, 6, 1)) +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "differences in number of items endorsed (out of 6)")
```

```{r}
figSUPP5_plots <- plot_grid(figSUPP5a_plot, figSUPP5b_plot,
                            ncol = 1, labels = "AUTO")
```


```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP5_with_caption <- add_sub(figSUPP5_plots, str_wrap("Figure SUPP5: Differences in the number of mental capacity items (out of 6) endorsed across the three domains (BODY minus HEART, BODY minus MIND, and MIND minus HEART) by 4- to 9-year-old children and adults in Study 1, in which each participant assessed 20 mental capacities for one of nine target characters. We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 132), x = 0, hjust = 0)
ggdraw(figSUPP5_with_caption)
```

## Examine absolute difference scores

```{r}
d2_all_endorse_diff_abs_boot_anim <- d2_all_endorse_diff %>%
  left_join(d2_anim %>% distinct(character, anim_inan)) %>%
  group_by(age_group, anim_inan, comparison) %>%
  multi_boot_standard(col = "diff_01_abs") %>%
  ungroup()
```

```{r, include = T}
ggplot(d2_all_endorse_diff, 
       aes(x = diff_01_abs, color = age_group, fill = age_group)) +
  facet_grid(anim_inan ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/6, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r, include = T}
ggplot(d2_all_endorse_diff, 
       aes(x = diff_01_abs, color = age_group, fill = age_group)) +
  facet_grid(. ~ comparison) +
  geom_histogram(position = "identity", binwidth = 1/6, alpha = 0.5) +
  geom_vline(xintercept = 0.5, lty = 2) +
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 1, 0.5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  scale_color_brewer(palette = "Set1", direction = -1)
```

```{r}
figSUPP6a_plot <- d2_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d2_79 %>% distinct(subid, age) %>%
              full_join(d2_46 %>% distinct(subid, age))) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = diff_01_abs, 
             fill = anim_inan, color = anim_inan)) +
  facet_wrap(~ comparison) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F, alpha = 0.05) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d2_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 12), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d2_all_endorse_diff_abs_boot_anim %>% 
                    filter(age_group == "adults"),
                  aes(x = 12, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:10, 12), 
                     labels = c(paste0(4:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = seq(0, 6, 1)) +
  scale_color_manual(values = c("slategrey", "firebrick1"), na.value = "gray") +
  scale_fill_manual(values = c("slategrey", "firebrick1"), na.value = "gray") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "asbolute differences in number of items endorsed (out of 6)")
```


```{r}
d2_all_endorse_diff_abs_boot <- d2_all_endorse_diff %>%
  group_by(age_group, character, comparison) %>%
  multi_boot_standard(col = "diff_01_abs") %>%
  ungroup()
```

```{r}
figSUPP6b_plot <- d2_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d2_79 %>% distinct(subid, age) %>%
              full_join(d2_46 %>% distinct(subid, age))) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = diff_01_abs, 
             fill = character, color = character)) +
  facet_wrap(~ comparison) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F, alpha = 0.05) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d2_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 12), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d2_all_endorse_diff_abs_boot %>% 
                    filter(age_group == "adults"),
                  aes(x = 12, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:10, 12), 
                     labels = c(paste0(4:10, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = seq(0, 6, 1)) +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "asbolute differences in number of items endorsed (out of 6)")
```

```{r}
figSUPP6_plots <- plot_grid(figSUPP6a_plot, figSUPP6b_plot,
                            ncol = 1, labels = "AUTO")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP6_with_caption <- add_sub(figSUPP6_plots, str_wrap("Figure SUPP6: Absolute differences in the number of mental capacity items (out of 6) endorsed across the three domains (BODY minus HEART, BODY minus MIND, and MIND minus HEART) by 4- to 9-year-old children and adults in Study 2, in which each participant assessed 20 mental capacities for one of nine target characters. We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP6_with_caption)
```


# Study 3

## Define buckets

```{r}
d3_buckets <- loadings_fun(efa_3_d3_ad) %>%
  mutate(factor = recode_factor(factor,
                                "F1" = "BODY",
                                "F2" = "HEART",
                                "F3" = "MIND")) %>%
  group_by(factor) %>%
  top_n(6, loading) %>%
  ungroup()
```

```{r}
d3_all_endorse <- d3_buckets %>%
  select(-loading) %>%
  left_join(d3_all) %>%
  mutate(endorse = ifelse(response_num > 0, 1, 0)) %>%
  group_by(age_group, subid, character, factor) %>%
  summarise(n = length(endorse),
            sum_endorse = sum(endorse, na.rm = T),
            prop_endorse = mean(endorse, na.rm = T)) %>%
  ungroup()
```

## Examine first-order age trends

```{r}
d3_all_endorse_boot <- d3_all_endorse %>%
  group_by(age_group, character, factor) %>%
  multi_boot_standard(col = "prop_endorse") %>%
  ungroup()
```

```{r}
figSUPP7_plot <- d3_all_endorse %>%
  filter(age_group != "adults") %>%
  left_join(d3_46 %>% distinct(subid, age)) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = prop_endorse, 
             fill = character, color = character, shape = character)) +
  facet_wrap(~ factor) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.03) +
  binomial_smooth(aes(weight = n), show.legend = F) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d3_all_endorse %>% filter(age_group == "adults"),
             aes(x = 6), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.03,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d3_all_endorse_boot %>% filter(age_group == "adults"),
                  aes(x = 6, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:6), 
                     labels = c(paste0(4:5, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = 0:6) +
  scale_color_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_fill_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_shape_manual(values = c(21, 22)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "number of items endorsed (out of 6)")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP7_with_caption <- add_sub(figSUPP7_plot, str_wrap("Figure SUPP7: Number of mental capacity items (out of 6) endorsed in each domain (BODY, HEART, and MIND) by 4- to 5-year-old children and adults in Study 3, in which each participant assessed 18 mental capacities for each of two target characters: a beetle (pink circles) and a robot (blue squares). We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP7_with_caption)
```

## Examine difference scores

```{r}
d3_all_endorse_diff <- d3_all_endorse %>%
  select(age_group, subid, character, factor, prop_endorse) %>%
  spread(factor, prop_endorse) %>%
  group_by(age_group, subid, character) %>%
  mutate(`BODY minus HEART` = BODY - HEART,
         `BODY minus MIND` = BODY - MIND,
         `MIND minus HEART` = MIND - HEART) %>%
  ungroup() %>% 
  select(-c(BODY, HEART, MIND)) %>%
  gather(comparison, difference, contains("min")) %>%
  mutate(diff_01 = (difference + 1)/2,
         diff_01_abs = abs(difference))
```

```{r}
d3_all_endorse_diff_boot <- d3_all_endorse_diff %>%
  group_by(age_group, character, comparison) %>%
  multi_boot_standard(col = "diff_01") %>%
  ungroup()
```

```{r}
figSUPP8_plot <- d3_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d3_46 %>% distinct(subid, age)) %>%
  filter(!is.na(age)) %>%
  mutate(y = (difference + 6)/12) %>%
  ggplot(aes(x = age, y = diff_01, 
             fill = character, color = character, shape = character)) +
  facet_wrap(~ comparison) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d3_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 6), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d3_all_endorse_diff_boot %>% filter(age_group == "adults"),
                  aes(x = 6, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:6), 
                     labels = c(paste0(4:5, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/12), labels = seq(-6, 6, 1)) +
  scale_color_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_fill_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_shape_manual(values = c(21, 22)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "differences in number of items endorsed (out of 6)")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP8_with_caption <- add_sub(figSUPP8_plot, str_wrap("Figure SUPP8: Differences in the number of mental capacity items (out of 6) endorsed across the three domains (BODY minus HEART, BODY minus MIND, and MIND minus HEART) by 4- to 5-year-old children and adults in Study 3, in which each participant assessed 18 mental capacities for each of two target characters: a beetle (pink circles) and a robot (blue squares). We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP8_with_caption)
```

## Examine absolute difference scores

```{r}
d3_all_endorse_diff_abs_boot <- d3_all_endorse_diff %>%
  group_by(age_group, character, comparison) %>%
  multi_boot_standard(col = "diff_01_abs") %>%
  ungroup()
```

```{r}
figSUPP9_plot <- d3_all_endorse_diff %>%
  filter(age_group != "adults") %>%
  left_join(d3_46 %>% distinct(subid, age)) %>%
  filter(!is.na(age)) %>%
  mutate(y = (difference + 6)/12) %>%
  ggplot(aes(x = age, y = diff_01_abs, 
             fill = character, color = character, shape = character)) +
  facet_wrap(~ comparison) +
  geom_jitter(alpha = 0.4, width = 0, height = 0.015) +
  binomial_smooth(aes(weight = 1), show.legend = F) +
  # geom_smooth(method = "glm",
  #             method.args = list(family = "binomial")) +
  geom_point(data = d3_all_endorse_diff %>% filter(age_group == "adults"),
             aes(x = 6), alpha = 0.4, show.legend = F,
             position = position_jitterdodge(dodge.width = 0.5,
                                             jitter.height = 0.015,
                                             jitter.width = 0.25)) +
  geom_pointrange(data = d3_all_endorse_diff_abs_boot %>% 
                    filter(age_group == "adults"),
                  aes(x = 6, y = mean, ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.5), show.legend = F,
                  color = "black", fatten = 5) +
  scale_x_continuous(breaks = c(4:6), 
                     labels = c(paste0(4:5, "y"), "adults")) +
  scale_y_continuous(breaks = seq(0, 1, 1/6), labels = seq(0, 6, 1)) +
  scale_color_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_fill_manual(values = c("#fb9a99", "#1f78b4")) +
  scale_shape_manual(values = c(21, 22)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  labs(y = "asbolute differences in number of items endorsed (out of 6)")
```

```{r, include = T, fig.width = 6, fig.asp = 0.7}
figSUPP9_with_caption <- add_sub(figSUPP9_plot, str_wrap("Figure SUPP8: Absolute differences in the number of mental capacity items (out of 6) endorsed across the three domains (BODY minus HEART, BODY minus MIND, and MIND minus HEART) by 4- to 5-year-old children and adults in Study 3, in which each participant assessed 18 mental capacities for each of two target characters: a beetle (pink circles) and a robot (blue squares). We defined each domain by the 6 items that loaded the most positively on the corresponding factor in an exploratory factor analysis of adults' responses, and we considered responses of either 'yes' or 'kinda' (but not 'no') to be endorsements. Lines correspond to logistic regressions considering children's scores alone. Error bars are bootstrapped 95% confidence intervals on adults' scores.", 130), x = 0, hjust = 0)
ggdraw(figSUPP9_with_caption)
```


