---
title: "Quick dimkid check"
output: html_notebook
---

We were using the wrong "maximal" model! This is a quick notebook to check what we see when we use the right maximal model to determine how many factors to extract.

```{r global_options, include = F}
knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F)
```

```{r libraries, include = F}
library(tidyverse)
library(lubridate)
library(psych)
library(rms)
library(dendextend)
```

```{r functions, include = F}
# make function to clean up kid data from US
clean_kid_us_fun <- function(df, n_trials, age_lower, age_upper) {
  
  if(!("age" %in% names(df))) {
    df <- df %>%
      mutate(age = NA)
  }
  
  df_clean <- df %>%
    mutate(dob = parse_datetime(dateOfBirth, "%m/%d/%y"),
           dot = parse_datetime(gsub("2017", "17", dateOfTest), "%m/%d/%y"),
           age = ifelse(is.na(age),
                        interval(start = dob, end = dot) /
                          duration(num = 1, units = "years"),
                        age)) %>%
    filter(trialNum <= n_trials) %>%
    filter((age >= age_lower & age < age_upper + 1) | # outside of age range
             is.na(age), # missing age
           (rt >= 250 | is.na(rt)), # fast RTs
           response %in% c("no", "kinda", "yes"), # skipped trials
           !is.na(subid), !is.na(capacity)) %>%
    mutate(responseNum = recode(response,
                                "no" = 0,
                                "kinda" = 0.5,
                                "yes" = 1),
           responseNum = as.numeric(responseNum)) %>%
    distinct(subid, capacity, responseNum) %>%
    mutate(capacity = recode(capacity,
                             "conscious" = "awareness",
                             "embarrassed" = "embarrassment",
                             "guilt" = "guilt",
                             "happy" = "happiness",
                             "love" = "love",
                             "pain" = "pain",
                             "pride" = "pride",
                             "depressed" = "sadness",
                             "fear" = "fear",
                             "nauseated" = "nausea",
                             "tired" = "fatigue",
                             "reasoning" = "figuring_out",
                             "angry" = "anger",
                             "hungry" = "hunger",
                             "disrespected" = "hurt_feelings",
                             "choices" = "choice",
                             "remembering" = "memory",
                             "temperature" = "temperature",
                             "depth" = "depth",
                             "odors" = "smell")) %>%
    spread(capacity, responseNum) %>%
    remove_rownames() %>%
    column_to_rownames("subid")
  
  return(df_clean)
  
}

# make function to determine max n_factors, given n_obs variables
max_fact_fun <- function(p) {
  
  s_moments <- function(p) {p*(p+1)/2}
  param_est <- function(p, k) {p*k + p - (k*(k-1)/2)}
  check_ok <- function(p, k) {
    a <- (p-k)^2
    b <- p+k
    return(ifelse(a>b, TRUE, FALSE))
  }
  
  df_check <- data.frame()
  for(i in 1:p){
    df_check[i,"check"] <- check_ok(p,i)
  }
  
  max <- df_check %>% filter(check) %>% nrow()
  return(max)
  
}

# make function to implement factor retention criteria
reten_fact_fun <- function(df, rot) {
  
  max_efa <- fa(df, nfactors = max_fact_fun(ncol(df)), rotate = "none")
  max_vacc <- max_efa$Vaccounted %>%
    data.frame() %>%
    rownames_to_column("stat") %>%
    gather(factor, value, -stat) %>%
    spread(stat, value) %>%
    filter(`SS loadings` > 1, `Proportion Explained` > 0.05)
  n_reten1 <- nrow(max_vacc)
  
  reten_efa <- fa(df, nfactors = n_reten1, rotate = rot)
  reten_loadings <- reten_efa$loadings[] %>%
    data.frame() %>%
    rownames_to_column("mc") %>%
    gather(factor, loading, -mc) %>%
    group_by(mc) %>%
    top_n(1, abs(loading)) %>%
    ungroup()
  n_reten2 <- reten_loadings %>%
    count(factor) %>%
    nrow()
    
  return(n_reten2)

}

# make function to plot heatmap of factor loadings
heatmap_fun <- function(df, n_factors, rot){
  
  # do efa
  efa <- fa(df, nfactors = n_factors, rotate = rot)
  
  # get factor loadings
  loadings <- efa$loadings[] %>%
    fa.sort() %>%
    data.frame() %>%
    rownames_to_column("mc") %>%
    rownames_to_column("order") %>%
    mutate(order = as.numeric(order)) %>%
    gather(factor, loading, -c(mc, order))
  
  # get shared variance explained
  vacc <- efa$Vaccounted %>%
    data.frame() %>%
    rownames_to_column("stat") %>%
    filter(stat == "Proportion Explained") %>%
    gather(factor, prop_var, -stat) %>%
    select(-stat)
  
  # plot it all
  plot <- ggplot(loadings %>% 
                   full_join(vacc) %>%
                   mutate(lab = paste0(factor, " (",
                                       format(100*round(prop_var, 2), 
                                              digits = 2),
                                       "%)")),
                 aes(x = lab, y = reorder(mc, desc(order)), fill = loading, 
                     label = format(round(loading, 2), nsmall = 2))) +
    geom_tile(color = "black") +
    geom_text(size = 3) +
    scale_x_discrete(position = "top") +
    scale_fill_distiller(limits = c(-1, 1), palette = "RdYlBu",
                         guide = guide_colorbar(barheight = 15)) +
    theme_minimal()
  
  return(plot)
  
}
```

```{r data, include = F, warning = FALSE}
# US adults, 2 characters
d_usad_2char <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/adults/us_run-01_2016-06-05_anonymized.csv") %>% 
  mutate(dateOfBirth = NA, dateOfTest = NA) %>%
  clean_kid_us_fun(n_trials = 40, age_lower = 18, age_upper = 100)

d_usad_2char_demo <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/adults/us_run-01_2016-06-05_anonymized.csv") %>%
  distinct(subid, charName)

# US adults, 9 character (NEED TO RUN)

# US 7-9yo, 2 characters
d_us79_2char <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/children/run-01_2017-07-24_anonymized.csv") %>% clean_kid_us_fun(n_trials = 40, age_lower = 7, age_upper = 9)

d_us79_2char_demo <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/children/run-01_2017-07-24_anonymized.csv") %>%
  distinct(subid, character, age) %>%
  filter((age >= 7 & age < 10) | is.na(age))

# US 7-9yo, 9 characters
d_us79_9char <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/children/run-02_2017-08-08_anonymized.csv") %>% clean_kid_us_fun(n_trials = 20, age_lower = 7, age_upper = 9)

d_us79_9char_demo <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/children/run-02_2017-08-08_anonymized.csv") %>%
  distinct(subid, character, dateOfBirth, dateOfTest) %>%
  mutate(dob = parse_datetime(dateOfBirth, "%m/%d/%y"),
         dot = parse_datetime(gsub("2017", "17", dateOfTest), "%m/%d/%y"),
         age = interval(start = dob, end = dot) /
           duration(num = 1, units = "years")) %>%
  filter((age >= 7 & age < 10) | is.na(age))

# US 4-6yo, 9 characters
d_us46_9char <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/children/run-03_2017-08-21_anonymized.csv") %>% clean_kid_us_fun(n_trials = 20, age_lower = 4, age_upper = 6)

d_us46_9char_demo <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/Dimkid/dimkid/data/children/run-03_2017-08-21_anonymized.csv") %>%
  distinct(subid, character, dateOfBirth, dateOfTest) %>%
  mutate(dob = parse_datetime(dateOfBirth, "%m/%d/%y"),
         dot = parse_datetime(gsub("2017", "17", dateOfTest), "%m/%d/%y"),
         age = interval(start = dob, end = dot) /
           duration(num = 1, units = "years")) %>%
  filter((age >= 4 & age < 7) | is.na(age))
```

#  US Adults, 2 characters

## Maximal structure, oblimin rotation

```{r, fig.width = 7, fig.asp = 0.5}
heatmap_fun(d_usad_2char, max_fact_fun(ncol(d_usad_2char)), "oblimin") +
  labs(title = "Factor loadings, maximal solution:  US Adults",
       subtitle = "2 characters, 40 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Reduced structure, oblimin rotation

```{r, fig.width = 3, fig.asp = 1.5}
heatmap_fun(d_usad_2char, reten_fact_fun(d_usad_2char, "oblimin"), "oblimin") +
  labs(title = "Factor loadings, after retention:  US Adults",
       subtitle = "2 characters, 40 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Alternative factor retention methods

```{r}
fa.parallel(d_usad_2char)
```

```{r, warnings = F}
VSS(d_usad_2char, n = max_fact_fun(ncol(d_usad_2char)), rotate = "oblimin", plot = F)
```

```{r, fig.width = 3, fig.asp = 1, include = F}
heatmap_fun(d_usad_2char, 4, "oblimin") +
  labs(title = "Factor loadings, parallel analysis:  US Adults",
       subtitle = "2 characters, 40 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Clustering within reduced factor space

```{r, fig.width = 4, fig.asp = 0.67}
# par(mar = c(1, 1, 1, 6))
clust <- fa(d_usad_2char, 
            reten_fact_fun(d_usad_2char, "oblimin"), "oblimin")$loadings[] %>%
  data.frame() %>%
  dist() %>%
  hclust()

clust %>%
  as.dendrogram() %>%
  set("labels_col", value = c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c",
                              "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", 
                              "#cab2d6", "#6a3d9a", "#ffff99", "#b15928"), 
      k = 6) %>%
  set("branches_lwd", 0.5) %>%
  # set("leaves_pch", 16) %>%
  # plot(horiz = T)
  as.ggdend() %>%
  ggplot(horiz = F) +
  geom_hline(yintercept = 2, lty = 2, color = "black") +
  coord_cartesian(ylim = c(-0.7, max(clust$height))) +
  labs(title = "Hierarchical clustering within reduced factor space:  US Adults",
       subtitle = "2 characters, 40 capacities, oblimin rotation")

rm(clust)
```


# 7-9yo US Children, 2 characters

## Maximal structure, oblimin rotation

```{r, fig.width = 7, fig.asp = 0.5}
heatmap_fun(d_us79_2char, max_fact_fun(ncol(d_us79_2char)), "oblimin") +
  labs(title = "Factor loadings, maximal solution: 7-9yo US Children",
       subtitle = "2 characters, 40 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Reduced structure, oblimin rotation

```{r, fig.width = 3, fig.asp = 1.5}
heatmap_fun(d_us79_2char, reten_fact_fun(d_us79_2char, "oblimin"), "oblimin") +
  labs(title = "Factor loadings, after retention: 7-9yo US Children",
       subtitle = "2 characters, 40 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Alternative factor retention methods

```{r}
fa.parallel(d_us79_2char)
```

```{r, warnings = F}
VSS(d_us79_2char, n = max_fact_fun(ncol(d_us79_2char)), rotate = "oblimin", plot = F)
```

```{r, fig.width = 3, fig.asp = 1, include = F}
heatmap_fun(d_us79_2char, 5, "oblimin") +
  labs(title = "Factor loadings, BIC retention: 7-9yo US Children",
       subtitle = "2 characters, 40 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Clustering within reduced factor space

```{r, fig.width = 4, fig.asp = 0.67}
# par(mar = c(1, 1, 1, 6))
clust <- fa(d_us79_2char, 
            reten_fact_fun(d_us79_2char, "oblimin"), "oblimin")$loadings[] %>%
  data.frame() %>%
  dist() %>%
  hclust()

clust %>%
  as.dendrogram() %>%
  # set("labels_col", value = c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c",
  #                             "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", 
  #                             "#cab2d6", "#6a3d9a", "#ffff99", "#b15928"), 
  #     k = 6) %>%
  set("labels_col", value = c("#fb9a99", "#e31a1c", "#a6cee3", "#1f78b4", 
                              "#b2df8a", "#33a02c"), 
      k = 6) %>%
  set("branches_lwd", 0.5) %>%
  # set("leaves_pch", 16) %>%
  # plot(horiz = T)
  as.ggdend() %>%
  ggplot(horiz = F) +
  geom_hline(yintercept = 2, lty = 2, color = "black") +
  coord_cartesian(ylim = c(-0.7, max(clust$height))) +
  labs(title = "Hierarchical clustering within reduced factor space: 7-9yo US Children",
       subtitle = "2 characters, 40 capacities, oblimin rotation")

rm(clust)
```


# 7-9yo US Children, 9 characters

## Maximal structure, oblimin rotation

```{r, fig.width = 4, fig.asp = 0.67}
heatmap_fun(d_us79_9char, max_fact_fun(ncol(d_us79_9char)), "oblimin") +
  labs(title = "Factor loadings, maximal solution: 7-9yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Reduced structure, oblimin rotation

```{r, fig.width = 3, fig.asp = 1}
heatmap_fun(d_us79_9char, reten_fact_fun(d_us79_9char, "oblimin"), "oblimin") +
  labs(title = "Factor loadings, after retention: 7-9yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```


## Alternative factor retention methods

```{r}
fa.parallel(d_us79_9char)
```

```{r}
VSS(d_us79_9char)
```

```{r, fig.width = 3, fig.asp = 1, include = F}
heatmap_fun(d_us79_9char, 4, "oblimin") +
  labs(title = "Factor loadings, 4-factor solution: 7-9yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Clustering within reduced factor space

```{r, fig.width = 4, fig.asp = 0.67}
# par(mar = c(1, 1, 1, 6))
clust <- fa(d_us79_9char, 
            reten_fact_fun(d_us79_9char, "oblimin"), "oblimin")$loadings[] %>%
  data.frame() %>%
  dist() %>%
  hclust()

clust %>%
  as.dendrogram() %>%
  set("labels_col", value = c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c",
                              "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", 
                              "#cab2d6", "#6a3d9a", "#ffff99", "#b15928"), 
      k = 4) %>%
  set("branches_lwd", 0.5) %>%
  # set("leaves_pch", 16) %>%
  # plot(horiz = T)
  as.ggdend() %>%
  ggplot(horiz = F) +
  geom_hline(yintercept = 2, lty = 2, color = "black") +
  coord_cartesian(ylim = c(-0.7, max(clust$height))) +
  labs(title = "Hierarchical clustering within reduced factor space: 7-9yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation")

rm(clust)
```

# 4-6yo US Children

## Maximal structure, oblimin rotation

```{r, fig.width = 4, fig.asp = 0.67}
heatmap_fun(d_us46_9char, max_fact_fun(ncol(d_us46_9char)), "oblimin") +
  labs(title = "Factor loadings, maximal solution: 4-6yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Reduced structure, oblimin rotation

```{r, fig.width = 3, fig.asp = 1}
heatmap_fun(d_us46_9char, reten_fact_fun(d_us46_9char, "oblimin"), "oblimin") +
  labs(title = "Factor loadings, after retention: 4-6yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```


## Alternative factor retention methods

```{r}
fa.parallel(d_us46_9char)
```

```{r, fig.width = 3, fig.asp = 1}
heatmap_fun(d_us46_9char, 2, "oblimin") +
  labs(title = "Factor loadings, parallel analysis: 4-6yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

```{r}
VSS(d_us46_9char)
```

```{r, fig.width = 3, fig.asp = 1}
heatmap_fun(d_us46_9char, 1, "oblimin") +
  labs(title = "Factor loadings, minimizing BIC: 4-6yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

```{r, fig.width = 3, fig.asp = 1, include = F}
heatmap_fun(d_us46_9char, 4, "oblimin") +
  labs(title = "Factor loadings, 4-factor solution: 4-6yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation",
       x = "", y = "", fill = "")
```

## Clustering within reduced factor space

```{r, fig.width = 4, fig.asp = 0.67}
# par(mar = c(1, 1, 1, 6))
clust <- fa(d_us46_9char, 
            reten_fact_fun(d_us46_9char, "oblimin"), "oblimin")$loadings[] %>%
  data.frame() %>%
  dist() %>%
  hclust()

clust %>%
  as.dendrogram() %>%
  set("labels_col", 
      # value = colorRampPalette(solarized_pal()(8))(20),
      value = c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c",
                "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00",
                "#cab2d6", "#6a3d9a", "#ffff99", "#b15928"),
      k = 6) %>%
  set("branches_lwd", 0.5) %>%
  # set("leaves_pch", 16) %>%
  # plot(horiz = T)
  as.ggdend() %>%
  ggplot(horiz = F) +
  geom_hline(yintercept = 2, lty = 2, color = "black") +
  coord_cartesian(ylim = c(-0.7, max(clust$height))) +
  labs(title = "Hierarchical clustering within reduced factor space: 4-6yo US Children",
       subtitle = "9 characters, 20 capacities, oblimin rotation")

rm(clust)
```

# Changes in mental capacity attributions

```{r, fig.width = 5, fig.asp = 0.4}
efa_old <- fa(d_us79_9char, nfactors = 3, rotate = "oblimin")
efa_old$loadings[] %>% 
  fa.sort() %>% 
  data.frame() %>% 
  rownames_to_column("capacity") %>% 
  gather(factor, loading, -capacity) %>%
  group_by(factor) %>% 
  top_n(4, abs(loading)) %>%
  arrange(factor, desc(abs(loading))) %>%
  ungroup()

projected_young <- predict.psych(efa_old, d_us46_9char, d_us79_9char) %>%
  data.frame() %>%
  rownames_to_column("subid") %>%
  mutate(age_group = "4-6y") %>%
  full_join(d_us46_9char_demo %>% distinct(subid, character, age))

scores_old <- efa_old$scores %>%
  data.frame() %>%
  rownames_to_column("subid") %>%
  mutate(age_group = "7-9y") %>%
  full_join(d_us79_9char_demo %>% distinct(subid, character, age))

scores_all <- projected_young %>%
  full_join(scores_old) %>%
  filter(!is.na(character), !character %in% c("", " ")) %>%
  gather(factor, score, starts_with("MR")) %>%
  mutate(factor = factor(factor,
                         levels = c("MR1", "MR3", "MR2"),
                         labels = c("BODY", "HEART", "MIND")),
         character = factor(character,
                            levels = c("computer", "robot", "doll", 
                                       "teddy_bear", "beetle", "bird", 
                                       "mouse", "goat", "elephant")))

scores_all %>% distinct(age_group, character, subid) %>% count(character) %>% summarise(min = min(n), max = max(n))

ggplot(scores_all,
       aes(x = age, y = score,
           group = character, color = character, fill = character)) +
  facet_grid(~ factor) +
  geom_vline(xintercept = 7, lty = 3) +
  geom_point() +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_brewer(palette = "Paired", direction = 1) +
  scale_fill_brewer(palette = "Paired", direction = 1) +
  theme_minimal() +
  labs(x = "Age (y)",
       y = "Factor score (in older children's 3-factor space)",
       color = "Character", fill = "Character")
```

