---
title: "Appendix A: Additional EFA solutions"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes
   
# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

```{r}
# packages
source("./scripts/libraries.R")

# supporting functions
source("./scripts/efa_param.R")
source("./scripts/max_factors_efa.R")
source("./scripts/reten_fun.R")
source("./scripts/plot_fun.R")
source("./scripts/efa_fun.R")
source("./scripts/ms_fun.R")

# data scripts
source("./scripts/data_s1.R")
source("./scripts/data_s2_ad.R")
source("./scripts/data_s2_79.R")
source("./scripts/data_s3_ad.R")
source("./scripts/data_s3_79.R")
source("./scripts/data_s3_46.R")
source("./scripts/data_s4_ad.R")
source("./scripts/data_s4_46.R")
```

```{r}
# load in EFAs from Chapter II
# study 1
efa_par_d1a_ad <- readRDS(file = "./efas/efa_par_d1a_ad")
efa_bic_d1a_ad <- readRDS(file = "./efas/efa_bic_d1a_ad")
efa_wdm_d1a_ad <- readRDS(file = "./efas/efa_wdm_d1a_ad")

efa_par_d1b_ad <- readRDS(file = "./efas/efa_par_d1b_ad")
efa_bic_d1b_ad <- readRDS(file = "./efas/efa_bic_d1b_ad")
efa_wdm_d1b_ad <- readRDS(file = "./efas/efa_wdm_d1b_ad")

efa_par_d1c_ad <- readRDS(file = "./efas/efa_par_d1c_ad")
efa_bic_d1c_ad <- readRDS(file = "./efas/efa_bic_d1c_ad")
efa_wdm_d1c_ad <- readRDS(file = "./efas/efa_wdm_d1c_ad")

efa_par_d1d_ad <- readRDS(file = "./efas/efa_par_d1d_ad")
efa_bic_d1d_ad <- readRDS(file = "./efas/efa_bic_d1d_ad")
efa_wdm_d1d_ad <- readRDS(file = "./efas/efa_wdm_d1d_ad")

# study 2
efa_par_d2_ad <- readRDS(file = "./efas/efa_par_d2_ad")
efa_bic_d2_ad <- readRDS(file = "./efas/efa_bic_d2_ad")
efa_wdm_d2_ad <- readRDS(file = "./efas/efa_wdm_d2_ad")

efa_par_d2_79 <- readRDS(file = "./efas/efa_par_d2_79")
efa_bic_d2_79 <- readRDS(file = "./efas/efa_bic_d2_79")
efa_wdm_d2_79 <- readRDS(file = "./efas/efa_wdm_d2_79")

# study 3
efa_par_d3_ad <- readRDS(file = "./efas/efa_par_d3_ad")
efa_bic_d3_ad <- readRDS(file = "./efas/efa_bic_d3_ad")
efa_wdm_d3_ad <- readRDS(file = "./efas/efa_wdm_d3_ad")

efa_par_d3_79 <- readRDS(file = "./efas/efa_par_d3_79")
efa_bic_d3_79 <- readRDS(file = "./efas/efa_bic_d3_79")
efa_wdm_d3_79 <- readRDS(file = "./efas/efa_wdm_d3_79")

efa_par_d3_46 <- readRDS(file = "./efas/efa_par_d3_46")
efa_bic_d3_46 <- readRDS(file = "./efas/efa_bic_d3_46")
efa_wdm_d3_46 <- readRDS(file = "./efas/efa_wdm_d3_46")

# study 4
efa_par_d4_ad <- readRDS(file = "./efas/efa_par_d4_ad")
efa_bic_d4_ad <- readRDS(file = "./efas/efa_bic_d4_ad")
efa_wdm_d4_ad <- readRDS(file = "./efas/efa_wdm_d4_ad")

efa_par_d4_46 <- readRDS(file = "./efas/efa_par_d4_46")
efa_bic_d4_46 <- readRDS(file = "./efas/efa_bic_d4_46")
efa_wdm_d4_46 <- readRDS(file = "./efas/efa_wdm_d4_46")
```

# Appendix overview

In this appendix, I report additional exploratory factor analysis (EFA) results that were excluded from the main text of Chapter III, including: (a) unrotated versions of all of the EFA solutions reported in Chapter III; (b) oblimin-transformed (rather than varimax-rotated) versions of all of the EFA solutions reported in Chapter III; (c) additional varimax-rotated EFA solutions not reported in full in Chapter III because I deemd to be redundant with the reported solutions; and (d) EFA solutions for participants in Studies 1c and 4, broken out by which target character a participant assessed first vs. second.


# Unrotated solutions

Throughout this dissertation, beginning in Chapter III, I have reported EFA solutions after applying varimax rotation. This rotation, which maximizes the sum of the variances of the squared factor loadings, is intended to make factors more interpretable by producing "simple structure" (Thurstone, 1949). Here, for completeness, I present unrotated EFA solutions for all of the EFAs reported in Chapter III.

```{r}
# reset EFA parameters to default, then set chosen rotation to none
source("./scripts/efa_param.R")
chosen_rot <- "none"
```

## Study 1

```{r}
efa_3_d1a_ad_unrot <- fa_fun(d1a_ad_wide_i, 3)
efa_3_d1b_ad_unrot <- fa_fun(d1b_ad_wide_i, 3)
efa_3_d1c_ad_unrot <- fa_fun(d1c_ad_wide_i, 3)
efa_3_d1d_ad_unrot <- fa_fun(d1d_ad_wide_i, 3)
```

```{r}
# study 1a
plot_efa_3_d1a_ad_unrot <- heatmap_fun(efa_3_d1a_ad_unrot) +
  labs(title = "Study 1a", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

# study 1b
plot_efa_3_d1b_ad_unrot <- heatmap_fun(efa_3_d1b_ad_unrot) +
  labs(title = "Study 1b", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

# study 1c
plot_efa_3_d1c_ad_unrot <- heatmap_fun(efa_3_d1c_ad_unrot) +
  labs(title = "Study 1c", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

# study 1d
plot_efa_3_d1d_ad_unrot <- heatmap_fun(efa_3_d1d_ad_unrot) +
  labs(title = "Study 1d", subtitle = "Unrotated 3-factor solution") # +
  # theme(legend.position = "none")
```

```{r}
figureA.1 <- plot_grid(plot_efa_3_d1a_ad_unrot, plot_efa_3_d1b_ad_unrot, 
                       plot_efa_3_d1c_ad_unrot, plot_efa_3_d1d_ad_unrot,
                       labels = "AUTO", ncol = 4, rel_widths = c(1, 1, 1, 1.2))

figureA.1_cap <- add_sub(figureA.1, str_wrap("Figure A.1: Factor loadings from exploratory factor analyses of Study 1 (as reported in Chapter III), before rotation. All results are from US adult samples; see Chapter II for methods. (A) Study 1a. (B) Study 1b. (C) Study 1c. (D) Study 1d. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 210), x = 0, hjust = 0)
```

```{r figureA.1, include = T, fig.width = 9, fig.asp = 0.6}
ggdraw(figureA.1_cap)
```

## Study 2

```{r}
efa_3_d2_ad_unrot <- fa_fun(d2_ad_wide_i, 3)
efa_4_d2_ad_unrot <- fa_fun(d2_ad_wide_i, 4)
efa_3_d2_79_unrot <- fa_fun(d2_79_wide_i, 3)
```

```{r}
# adults
plot_efa_3_d2_ad_unrot <- heatmap_fun(efa_3_d2_ad_unrot) +
  labs(title = "Adults", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

plot_efa_4_d2_ad_unrot <- heatmap_fun(efa_4_d2_ad_unrot) +
  labs(title = "Adults", subtitle = "Unrotated 4-factor solution") +
  theme(legend.position = "none")

# children
plot_efa_3_d2_79_unrot <- heatmap_fun(efa_3_d2_79_unrot) +
  labs(title = "Chidlren, 7-9y", subtitle = "Unrotated 3-factor solution") # +
  # theme(legend.position = "none")
```

```{r}
figureA.2 <- plot_grid(plot_efa_3_d2_ad_unrot, plot_efa_4_d2_ad_unrot, 
                       plot_efa_3_d2_79_unrot, 
                       labels = "AUTO", ncol = 3, rel_widths = c(1, 1.2, 1.2))

figureA.2_cap <- add_sub(figureA.2, str_wrap("Figure A.2: Factor loadings from exploratory factor analyses of Study 2 (as reported in Chapter III), before rotation. (A) Results for US adults, retaining three factors. (B) Results for US adults, retaining four factors. (C) Results for US children ages 7-9y. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 210), x = 0, hjust = 0)
```

```{r figureA.2, include = T, fig.width = 9, fig.asp = 0.6}
ggdraw(figureA.2_cap)
```

## Study 3

```{r}
efa_3_d3_ad_unrot <- fa_fun(d3_ad_wide_i, 3)
efa_3_d3_79_unrot <- fa_fun(d3_79_wide_i, 3)
efa_2_d3_46_unrot <- fa_fun(d3_46_wide_i, 2)
efa_3_d3_46_unrot <- fa_fun(d3_46_wide_i, 3)
```

```{r}
# adults
plot_efa_3_d3_ad_unrot <- heatmap_fun(efa_3_d3_ad_unrot) +
  labs(title = "Adults", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

# older children
plot_efa_3_d3_79_unrot <- heatmap_fun(efa_3_d3_79_unrot) +
  labs(title = "Older children, 7-9y", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

# younger children
plot_efa_3_d3_46_unrot <- heatmap_fun(efa_3_d3_46_unrot) +
  labs(title = "Younger children, 4-6y", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

plot_efa_2_d3_46_unrot <- heatmap_fun(efa_2_d3_46_unrot) +
  labs(title = "Younger children, 4-6y", subtitle = "Unrotated 2-factor solution") +
  theme(legend.position = "none")
```

```{r}
figureA.3 <- plot_grid(plot_efa_3_d3_ad_unrot, plot_efa_3_d3_79_unrot,
                       plot_efa_3_d3_46_unrot, plot_efa_2_d3_46_unrot,
                       labels = "AUTO", ncol = 4, rel_widths = c(1, 1, 1, 1))

figureA.3_cap <- add_sub(figureA.3, str_wrap("Figure A.3: Factor loadings from exploratory factor analyses of Study 3 (as reported in Chapter III), before rotation. (A) Results for US adults. (B) Results for US children ages 7-9y. (C) Results for US children ages 4-6y, retaining three factors. (D) Results for US children ages 4-6y, retaining two factors. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 210), x = 0, hjust = 0)
```

```{r figureA.3, include = T, fig.width = 9, fig.asp = 0.6}
ggdraw(figureA.3_cap)
```

## Study 4

```{r}
efa_3_d4_ad_unrot <- fa_fun(d4_ad_wide_i, 3)
efa_3_d4_46_unrot <- fa_fun(d4_46_wide_i, 3)
efa_4_d4_46_unrot <- fa_fun(d4_46_wide_i, 4)
```

```{r}
# adults
plot_efa_3_d4_ad_unrot <- heatmap_fun(efa_3_d4_ad_unrot) +
  labs(title = "Adults", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

# younger children
plot_efa_3_d4_46_unrot <- heatmap_fun(efa_3_d4_46_unrot) +
  labs(title = "Children, 4-5y", subtitle = "Unrotated 3-factor solution") +
  theme(legend.position = "none")

plot_efa_4_d4_46_unrot <- heatmap_fun(efa_4_d4_46_unrot) +
  labs(title = "Children, 4-5y", subtitle = "Unrotated 4-factor solution") +
  theme(legend.position = "none")
```

```{r}
figureA.4 <- plot_grid(plot_efa_3_d4_ad_unrot, plot_efa_3_d4_46_unrot, 
                       plot_efa_4_d4_46_unrot,
                       labels = "AUTO", ncol = 3, rel_widths = c(1, 1, 1.4))

figureA.4_cap <- add_sub(figureA.4, str_wrap("Figure A.4: Factor loadings from exploratory factor analyses of Study 4 (as reported in Chapter III), before rotation. (A) Results for US adults. (B) Results for US children ages 4-5y, retaining three factors. (C) Results for US children ages 4-5y, retaining four factors. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 210), x = 0, hjust = 0)
```

```{r figureA.4, include = T, fig.width = 9, fig.asp = 0.6}
ggdraw(figureA.4_cap)
```

```{r}
# reset EFA parameters to default
source("./scripts/efa_param.R")
```


# Varimax-rotated solutions previously deemed redundant

In Chapter III, I focused my interpretation on a subset of the EFA solutions suggested by the three factor retention protocols, excluding those solutions in which additional factors were redundant with the 3-factor (BODY-HEART-MIND) solution. These additional factors tend to explain very little of the shared variance; tend not to be the dominant factor (the factor with the strongest absolute factor loading) for many, if any, mental capacities; and tend to have very weak factor loadings. I include them here for completeness.

## Study 1

The factor retention criteria employed in Weisman et al. (2017) suggested retaining 3 factors for all of the studies included in Study 1; see Chapter III. In contrast, parallel analysis suggested retaining 4 factors (instead of 3) for Studies 1b and 1d; minimizing BIC suggested retaining 4 factors (instead of 3) for Study 1c, and 5 factors (instead of 3) for Studies 1a, 1b, and 1d. See Figure A.5.

```{r}
# study 1a
plot_efa_bic_d1a_ad <- heatmap_fun(efa_bic_d1a_ad, 
                                   c("BODY", "HEART", "MIND", 
                                     "Factor 4", "Factor 5")) +
  labs(title = "Study 1a", subtitle = "5-factor solution") +
  theme(legend.position = "none")

# study 1b
plot_efa_par_d1b_ad <- heatmap_fun(efa_par_d1b_ad, 
                                   c("BODY", "HEART", "MIND", "Factor 4")) +
  labs(title = "Study 1b", subtitle = "4-factor solution") +
  theme(legend.position = "none")

plot_efa_bic_d1b_ad <- heatmap_fun(efa_bic_d1b_ad, 
                                   c("BODY", "HEART", "MIND", 
                                     "Factor 4", "Factor 5")) +
  labs(title = "Study 1b", subtitle = "5-factor solution") # +
  # theme(legend.position = "none")

# study 1c
plot_efa_bic_d1c_ad <- heatmap_fun(efa_bic_d1c_ad, 
                                   c("BODY", "HEART", "MIND", "Factor 4")) +
  labs(title = "Study 1c", subtitle = "4-factor solution") +
  theme(legend.position = "none")

# study 1d
plot_efa_par_d1d_ad <- heatmap_fun(efa_par_d1d_ad, 
                                   c("BODY", "HEART", "MIND", "Factor 4")) +
  labs(title = "Study 1d", subtitle = "4-factor solution") +
  theme(legend.position = "none")

plot_efa_bic_d1d_ad <- heatmap_fun(efa_bic_d1d_ad, 
                                   c("BODY", "HEART", "MIND", 
                                     "Factor 4", "Factor 5")) +
  labs(title = "Study 1d", subtitle = "5-factor solution") # +
  # theme(legend.position = "none")
```

```{r}
figureA.5 <- plot_grid(plot_efa_bic_d1a_ad, 
                       plot_efa_par_d1b_ad, plot_efa_bic_d1b_ad, 
                       plot_efa_bic_d1c_ad,
                       plot_efa_par_d1d_ad, plot_efa_bic_d1d_ad,
                       labels = "AUTO", ncol = 3, rel_widths = c(1, 1, 1.2))

figureA.5_cap <- add_sub(figureA.5, str_wrap("Figure A.5: Factor loadings from additional exploratory factor analyses of Study 1, not reported in Chapter III. All results are from US adult samples; see Chapter II for methods. (A) Study 1a, solution suggested by minimizing BIC. (B) Study 1b, solution suggested by parallel analysis. (C) Study 1b, solution suggested by minimizing BIC. (D) Study 1c, solution suggested by minimizing BIC. (E) Study 1d, solution suggested by parallel analysis. (F) Study 1d, solution suggested by minimizing BIC. In this and all figures portraying factor loadings, factors have been plotted in the same order (BODY, HEART, MIND), when applicable, to facilitate comparison across studies. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 200), x = 0, hjust = 0)
```

```{r figureA.5, include = T, fig.width = 9, fig.asp = 1}
ggdraw(figureA.5_cap)
```

## Study 2

All of the EFA solutions suggested by the three factor retention protocols are reported in full in Chapter III.

## Study 3

The factor retention criteria employed in Weisman et al. (2017) suggested retaining 3 factors for all of the age groups included in Study 3; see Chapter III. In contrast, parallel analysis suggested retaining 2 factors (instead of 3) for younger children; and minimizing BIC suggested retaining 4 factors (instead of 3) for adults, and 1 factor (i.e., a "null" solution) for younger children (ages 4-6y). See Figure A.6.

```{r}
# study 3
plot_efa_bic_d3_ad <- heatmap_fun(efa_bic_d3_ad, 
                                   c("BODY", "HEART", "MIND", "Factor 4")) +
  labs(title = "Study 3: Adults", subtitle = "5-factor solution") +
  theme(legend.position = "none")

plot_efa_bic_d3_46 <- heatmap_fun(efa_bic_d3_46, ) +
  labs(title = "Study 3: Younger children, 4-6y", 
       subtitle = "1-factor (null) solution") #+
  # theme(legend.position = "none")
```

```{r}
figureA.6 <- plot_grid(plot_efa_bic_d3_ad, plot_efa_bic_d3_46,
                       labels = "AUTO", ncol = 2, rel_widths = c(1, 1))

figureA.6_cap <- add_sub(figureA.6, str_wrap("Figure A.6: Factor loadings from additional exploratory factor analyses of Study 3, not reported in Chapter III. See Chapter II for methods. (A) Adults, solution suggested by minimizing BIC. (B) Younger children (4-6y), 'null' solution suggested by minimizing BIC. In this and all figures portraying factor loadings, factors have been plotted in the same order (BODY, HEART, MIND), when applicable, to facilitate comparison across studies. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 115), x = 0, hjust = 0)
```

```{r figureA.6, include = T, fig.width = 5, fig.asp = 1}
ggdraw(figureA.6_cap)
```

## Study 4

All of the EFA solutions suggested by the three factor retention protocols are reported in full in Chapter III, with the exception of the 1-factor ("null") solution suggested by minimizing BIC for younger children (4-5y). See Figure A.7.

```{r}
# study 4
plot_efa_bic_d4_46 <- heatmap_fun(efa_bic_d4_46, ) +
  labs(title = "Study 4: Younger children, 4-5y", 
       subtitle = "1-factor (null) solution") # +
  # theme(legend.position = "none")
```

```{r}
figureA.7 <- plot_efa_bic_d4_46

figureA.7_cap <- add_sub(figureA.7, str_wrap("Figure A.7: Factor loadings from the 'null' solution suggested by minimizing BIC for younger children (4-5y) in Study 4. See Chapter II for methods, and Chapter III for other EFA solutions for this study. A factor loading of +1 indicates a perfectly positive relationship between mental capacity and underlying construct; a loading of -1 indicates a perfectly negative relationship.", 30), x = 0, hjust = 0)
```

```{r figureA.7, include = T, fig.width = 2, fig.asp = 1.8}
ggdraw(figureA.7_cap)
```




