---
title: "Chapter I: Theoretical foundations"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes

# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

The act of attributing mental life to other beings in the world is a fundamental part of human experience: From early in life, we look at others around us and see not just physical objects, but people, minds, with sensations, emotions, thoughts, and memories of their own. Viewing others in this way lays the foundation for our social lives and our behavior toward others. We might infer our friends’ goals and try to help, or identify things that others have forgotten or misunderstood and correct them; we delight in each other’s happiness, seek comfort from each other in times of sadness, and plan our actions to avoid (or to appear to avoid) causing others emotional or physical pain. In this sense, representations of mental life are at the core of human social life.

But mental life is complex, encompassing a wide range of experiences and abilities that stand in complicated relationships to each other and play a wide range of roles in the behaviors of and interactions between social beings. Capacities for perception, beliefs, desires, goals, thoughts, emotions, physiological sensations, and other mental states have some things in common—e.g., these mental states are commonly experienced as occurring privately "inside" an individual, without being directly accessible to anyone else (although they might facial expressions, words, actions, and other publicly observable behaviors)—but mental states also differ along many dimensions. Some mental states are closely related to specific bodily organs (e.g., people see things with their eyes, feel hunger in their stomachs), and others less obviously so (where do people experience belief?). Some are positively or negatively valenced (e.g., pain feels bad, happiness feels good), others are more neutral, or vary in valence depending on the circumstance (thought, olfaction). Some mental states involve taking in information about the environment (e.g., seeing, hearing), while others involve storing or updating that information (remembering, learning), or using it to bring about changes in the external world (planning, making choices). In a given social context, certain mental states might be considered more appropriate or socially productive than others (e.g., love vs. anger, guilt vs. pride, excitement vs. contentment [XX CITE TSAI on ideal affect]). And people might believe that certain mental capacities are shared by a wide range of entities (e.g., even insects might experience some kind of hunger; even robots might have a capacity for "memory," in some sense), while others are limited to a smaller subset of beings (perhaps only humans experience embarrassment) [XX CITE HASLAM on uniquely human].

This makes conceptual representations of mental life a fascinating case study of abstract reasoning and its development: How do people come to represent this complex conceptual space? This question has deep roots in cognitive and developmental psychology—but in attempting to address it, I draw inspiration from both ancient philosophers and modern social psychologists. In the following sections, I discuss the theoretical foundations of my approach, beginning with some groundbreaking recent work in social psychology.


# Theoretical foundations

## Recent work in social psychology on the "dimensions of mind perception"

A little over 10 years ago, a team of social psychologists published a brief but groundbreaking paper in the journal _Science_. The paper presented the results of a pioneering study in which adult participants were asked to compare the mental capacities of a variety of humans, animals, and other target characters. From these assessments, the authors derived two axes of variability in participants' responses: a dimension they called “experience,” which captured the extent to which participants considered a character to be capable of hunger, fear, pain, pleasure, rage, desire, personality, consciousness, pride, embarrassment, and joy; and a dimension they called “agency,” which captured the extent to which participants considered a character is capable of self-control, morality, memory, emotion recognition, planning, communication, and thought. They called these two dimensions the "dimensions of mind perception" (XX CITE GRAY).

This study was ground-breaking in several ways: It was among the first generation of psychological studies to be conducted entirely online, which had allowed the authors to collect dataset including well over 2000 participants—at least an order of magnitude larger than most samples in psychology at the time. It was ambitious in scope, including questions about such deep and difficult concepts as consciousness, morality, and self-control, applied to such socially charged entities as a human fetus, a person in a persistant vegetative state, a "social robot," and God. It made use of an entirely data-driven (rather than hypothesis-driven) statistical procedure—principal components analysis—which just a decade or so earlier was so prohibitively expensive in terms of time and computational power that hardly any mainstream psychologists knew how conduct it. In other words, Gray et al. collected big data on a topic at the core of experimental philosophy and analyzed it using an unsupervised learning technique—all before "big data," "experimental philosophy," and "unsupervised learning" became the keywords that they are today. It was a groundbreaking piece of work, truly ahead of its time.

Of course, this single study was not without its flaws. Participants were allowed to choose which condition they participated in (e.g., choosing a survey that was described as asking them "to judge which character is more capable of experiencing physical or emotional pain" vs. one that was described as asking them "to judge which character is more capable of telling right from wrong and trying to do the right thing"; XX CITE GRAY SOM), and could opt to participate in as many of these conditions as they liked, in whatever order they chose—all of which could have introduced bias into participants' responses (e.g., if participants who were more interested in moral philosophy were more likely to opt into the "morality" condition). The target characters were presented alongside verbal descriptions that varied in their richness and detail (e.g., "Nicholas is a five-month-old baby" vs. "The Green Frog can be found throughout eastern North America. This classic 'pond frog' is medium-sized and green or bronze in color. Daily life includes seeking out permanent ponds or slow streams with plenty of vegetation"), and which sometimes included information about the correct way to assess to certain mental capacities (e.g., "Gerald [the patient in a persistant vegetative state] _does not appear to communicate with others or make purposeful movements_"; emphasis added) or anthropomorphic language—such as personal pronouns and names—that may have biased participants' construals of more controverisal entities (e.g., "_Toby_ is a two-year-old wild chimpanzee"; _Kismet_ [the 'social robot'] perceives a variety of natural social signals from sound and sight, and delivers _his_ own signals back to the human partner..."; emphasis added; XX CITE GRAY SOM). The data-processing pipeline involved using a very large dataset (2399 completed survey, each of which included 78 paired-comparison questions about the relative mental capacities of different characters, for a total of `r 2399 * 78` datapoints) to construct a much smaller dataset (13 target characters, each associated with a mean relative score for 18 mental capacities, for a total of `r 13 * 18` datapoints) before conducting principal components analysis, which (in principle) constrained the possible outcomes of the analysis—including rendering it extremely unlikely to detect more than one or two "dimension." The interpretation of this analysis neglected to account for the fact that the first of these "dimensions" (experience) accounted for fully 88% of the variance in characters' mean mental capacity scores, which calls into question whether this analysis detected any meaningful multi-dimensional structure in the first place.

Aside from these critiques, upon deeper reflection on the details of the methods employed in Gray et al.'s work—in which each participant engaged in a series of paired comparisons between different target characters while focusing on a single mental capacity for the duration of the survey—I came to believe that this study did not actually assess people’s intuitions about the similarities and differences _among mental capacities_, but rather their intuitions about the similarities and differences _among social beings_. In the original publication of the first set of studies included in this dissertation (referred to here as Studies 1a-1d),
my co-authors and I argued that assessing people’s intuitions about the structure of mental life requires a sensitive measure that encourages participants to think about the connections and divisions among mental capacities themselves: Which capacities "go together," and which capacities are more distinct? (See XX CITE WEISMAN et al., 2017).

Despite my critiques of this particular study, I continue to consider Gray et al.'s work to be a major inspiration for my own—particularly in its expansive scope and its pioneering use of a bottom-up approach to questions of conceptual representation. 

Many investigations of ordinary people's representations of "the mind" are focused on beliefs and understanding within particular domains, such as "cognition" (e.g., XX CITE SCHWANENFLUGEL) or "emotion" (XX CITE NOOK). In contrast, Gray et al. included an unprecedentedly wide variety of "mental capacities" in their study, from physiological sensations like hunger and pain to capacities for moral reasoning (and everything in between). In my view, this expansive scope is critical for getting a holistic sense of this complicated domain. 

I have also found their data-driven approach—using unsupervised learning techniques to reconstruct participants' representations of a conceptual domain "from the bottom up," rather than establishing and testing a priori theories of conceptual structure—to be liberating and (in my view) very productive. Such a bottom-up approach has tremendous potential for elucidating the kinds of deep conceptual structures that are difficult for participants to report on directly and for experimenters to anticipate a priori. (For other examples of bottom-up approaches to conceptual related to "mental life," see XX CITE HASLAM on beliefs about the mental capacities that make up human nature vs. those that are uniquely human; XX RIPS & CONRAD, SCHWANENFLUGEL on the logical relationships among different cognitive abilities; and—most recently—XX NOOK on the dimensions of children's understanding of emotions and affective states.)

Gray et al.'s particular implementation of this bottom-up approach was particularly compelling to me as a developmental psychologist because of its simplicity. Participants in their study answered a series of relatively straightforward, concrete questions, which drew on their intuitions about familiar entities in the world (e.g., “Which character do you think is more capable of feeling joy?"). Such questions are likely to be easier, quicker, and more enjoyable for young children than the demanding metacognitive or metalinguistic tasks that one could imagine employing (e.g., deciding how similar two sentences are “based on the ways you use your mind in each one”; Fabricius et al., 1989, p. 1281).


## Rich traditions in cognitive and developmental psychology

XX __REVISE SCRAPS PASTED BELOW__

Decades of work on cognitive and social development has made it clear that early and middle childhood is a time of rapid change in children’s understanding of the vast range of experiences and abilities that might be considered part of “mental life.” In the domain of lay psychology and “theory of mind,” hundreds of studies have documented dramatic shifts in children’s abilities to take others’ perspectives, predict and explain people’s emotions, represent false beliefs, and integrate representations of beliefs and intentions in evaluating moral responsibility (for reviews, see Flavell, 1999; Wellman, 2015). The period between 4-10y of age has also been the focus of a rich tradition of work on lay biology extending back nearly a century (e.g., Carey, 1985; Medin et al., 2010; Piaget, 1929), which has included forays into children’s understanding of which beings in the world are susceptible to physiological sensations like hunger, pain, and fatigue. Taken together, this body of work makes the case that becoming a sophisticated reasoner—and particularly a sophisticated social reasoner—requires substantial refinement of one’s representations of others’ experiences, beliefs, desires, and needs—in other words, changes in one’s conceptual representations of mental life.

Developmental and cognitive psychologists have made great progress in understanding how people make sense of other minds by postulating distinct representations of such categories as “perceptions,” “beliefs,” “desires,” and “emotions” (for reviews, see Flavell, 1999; Wellman, 2015). Do these categories correspond to children’s own developing understanding of the structure of mental life? How do children conceive of the connections and distinctions among mental states, and how does this conceptual structure shape their understanding of the various humans, animals, technologies, and other “beings” in the world around them?

In the current studies, we set out to derive this conceptual structure and chart its development using an exploratory, “bottom-up” approach that surfaces conceptual connections and distinctions from data without reference to a particular pre-specified hypothesis or theory. XX __CONNECT BACK TO PREVIOUS SECTION__

From our perspective, this approach has two major advantages: It can reveal conceptual structure without requiring participants to articulate it themselves; and the conceptual structures revealed by this approach can, in principle, differ dramatically from the assumptions of a research team. These are especialaly compelling advantages in the domain of conceptual development—in which, by definition, participants struggle to introspect and articulate their reasoning, and findings often conflict with adult intuitions. Anticipated and unanticipated axes of comparison. XX __CHECK REDUNDANCIES WITH PREVIOUS SECTION__

## Ancient approaches to characterizing the "mind" or "soul"

XX __REVISE SCRAPS PASTED BELOW__

Curiosity about the nature of the "mind" or "soul" extends back to antiquity.

Plato: tripartite distinction between appetite, spirit, and reason

Aristotle: three souls (nutritive, XX, XX)

Buddha: five aggregates of senstient beings (material form, feelings, perceptions, impulses, consciousness)


# The current project: Exploring development in three aspects of conceptual representations of mental life

My goal in this dissertation is to characterize the development of conceptual representations of mental life in the modern US context. I aim to unite the "bottom-up" approach and sweeping scope provided by recent work in social psychology with the framework of "lay concepts" and "folk theories" that has emerged from cognitive and developmental psychology over the past several decades (both reviewed in the previous section). In addition to providing a case study of abstract reasoning and its development, I believe this work has the potential to shed new light on the development of the animate-inanimate distinction—a topic with a rich history in psychology extending back to Piaget. 

Indeed, the roots of this topic are even older than the field of psychology itself. Drawing inspiration from the works of  Plato, Aristotle, and the Buddha on the nature of the "mind" or "soul," I structure my exploration of _ordinary people's beliefs_ about the nature of mental life around three ontological questions that provide the backbone for this dissertation.

## Question #1: _What are the components, or "conceptual units," that anchor representations of mental life at different points in development?_

As described early in this chapter ("Ancient approaches to characterizing the 'mind' or 'soul'"), XX.

## Question #2: _How are these conceptual units organized in relation to each other, and how does this organization change over development?_

As described early in this chapter ("Ancient approaches to characterizing the 'mind' or 'soul'"), XX.

## Question #3: _How do people of different ages deploy their conceptual representations of mental life to reason about specific entities in the world—namely, animate beings vs. inanimate objects?_ 

As described early in this chapter ("Ancient approaches to characterizing the 'mind' or 'soul'"), XX.


# Overview

The remainder of this dissertation is devoted to describing empirical findings that, I believe, shed light on each of these three key questions about conceptual representations of mental life in the modern US context. I begin by identifying "conceptual units" at three points in development: early childhood (4-6y), middle chidlhood (7-9y), and adulthood (Chapter III). Next, I explore the relationships among these conceptual units, and how these relationships might evolve and change over this period of development (Chapter IV). I then consider the deployment or application of these conceptual representations in one aspect of social reasoning, using the apparent conceptual structure established in Chapters III-IV to shed light on children's developing mental capacity attributions to animate beings vs. inaimate objects (Chatper V). Finally, I synthesize my findings from these three lines of inquiry and step back to reflect on how these three aspects of conceptual development might be related to one other, what this case study of representations of mental life might reveal about conceptual development more broadly, and the potential consequences of these representations of mental life in children's social development (Chapter VI). 

First, in Chapter II, I provide an overview of my general empirical approach and the specific methods I employed in the four large-scale studies included in this dissertation.

