---
title: "Chapter I: Theoretical foundations"
output:
  word_document:
    reference_docx: "./word-styles-reference.docx"
always_allow_html: yes
bibliography: ./bibliography/dissbib.bib
csl: ./bibliography/apa.csl
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r, include = F}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes

# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

The act of attributing mental life to other beings in the world is a fundamental part of human experience: From early in life, we look at others around us and see not just physical objects, but people—minds—with sensations, emotions, thoughts, and memories of their own. 

Viewing others in this way lays the foundation for our social interactions. We might infer our friends’ goals and try to help, or anticipate and attempt to thwart the plans of a foe. When someone appears to have forgotten or misunderstood something, we might step in to correct them, or we might decide that they are capable of figuring things out on their own. We might delight in each other’s happiness, seek comfort from each other in times of sadness, and plan our actions to avoid (or to appear to avoid) causing others emotional or physical pain. These are just a few examples of how representations of *mental life*—goals, plans, thoughts, memories, reasoning abilities, emotions, perceptions, sensations, and the like—are at the core of human social life.

As these examples illustrate, mental life is complex, encompassing a wide range of experiences and abilities that vary along many dimensions. Some mental states are closely related to specific bodily organs (e.g., people see things with their eyes, feel hunger in their stomachs), and others less obviously so (where do people experience belief?). Some are positively or negatively valenced (e.g., pain feels bad, happiness feels good), others are more neutral, or vary in valence depending on the circumstance (thinking, smelling). Some mental states involve taking in information about the environment (e.g., seeing, hearing), while others involve storing or updating that information (remembering, learning), or using it to bring about changes in the external world (planning, making choices). In a given social context, certain mental states might be considered more appropriate or socially productive than others [e.g., love vs. anger, guilt vs. pride, excitement vs. contentment; @Tsai2007c]. And people might believe that certain mental capacities are shared by a wide range of entities (e.g., even insects might experience hunger; even robots might have a capacity for memory), while others are limited to a smaller subset of beings [perhaps only humans experience embarrassment; @Haslam2008]. 

How do people come to represent this complex conceptual space? This is the question I aim to address in this dissertation. Representations of mental life are a particularly fascinating case study of abstract reasoning and its development, with roots in ancient philosophy and connections to rich traditions of work in many sub-fields of psychology. In this chapter, I discuss these theoretical foundations. I begin with hints from developmental psychology that representations of mental life may undergo dramatic changes over the course of early and middle childhood.


# The possibility of conceptual change in representations of mental life

From the early work of Piaget through the present day, many seminal studies of cognitive development have touched on children's understanding of mental life. Long traditions of work on the animate-inanimate distinction, lay biology and psychology, and theory of mind all converge to suggest that the period of development between roughly 4-10 years of age is a time of rapid change in children's reasoning about many different experiences and abilities that might be considered part of mental life, as well as changes in children's tendency to attribute such capacities to fellow humans, animals, plants, natural objects, artifacts, and other entities in the world. These studies leave open, however, the question of whether these shifts in reasoning and attribution may be accompanied by changes to the underlying conceptual structure—the focus of this dissertation.

## Related developments in early and middle childhood

Early explorations of children's understanding of mental life were rooted in a more basic question: How do children understand "life" at all? Capacities for desires, goals, intentions, and other mental states are one of the key features that distinguish animate beings like humans and animals from inanimate objects [@Gelman1981a]. Indeed, beginning with Piaget's [-@Piaget1929] classic work on what he termed "childhood animism," attributions of such mental states to inanimate beings have been considered a hallmark of an immature understanding of life and animacy. Since then, many foundational figures in the field of cognitive development—Carey, Flavell, R. Gelman, S. Gelman, Keil, Medin, Spelke, Waxman, and Wellman, among others—have taken up the questions of whether, when, and why young children might attribute mental states to inanimate objects; as well as the question of what might drive the apparent decline of these "over-attributions" over development [see @Gelman1981a for an early review; and @Gelman2002, for a more recent review].

One pivotal moment in this tradition of work was the publication of Carey's [-@Carey1985b] seminal exploration of conceptual change in the domains of lay psychology and biology. Using a combination of Piagetian-style interviews and quantitative experiments, Carey documented dramatic changes in children's understanding of what it means for something to be alive; why living things do the things they do (e.g., eat, sleep, etc.); and which set of entities in the world have these properties. These studies suggested that young children [at least in the 20th-century urban US context; cf. @Herrmann2010; @Medin2010a] have an anthropocentric concept of life and life-related properties: Prior to roughly 7 years of age, children in Carey's studies appeared to base their assessment of whether entities are alive on judgments of their similarity to humans, and to ground their reasoning about activities like eating and sleeping in their understanding of human social-psychological behavior (e.g., we eat together at dinner time, we go to bed at night). Only older children appeared to draw on a more adult-like understanding of life as some kind of "vital force," grounded in and governing bodily processes and extending to a variety of entities that are quite different from humans. Over the course of early and middle childhood, Carey argued, children exchange an "animistic" theory of life for another, "vitalistic" one—in the process, demarcating the conceptual domain of living bodies ("lay biology") as separate from the conceptual domain of human social interactions ("lay psychology"). Together with other early work on the animate-inanimate distinction [e.g., @Dolgin1984; @Gelman1981a; @Gelman1983], Carey's findings have inspired a host of empirical studies of the development of lay biology and psychology, focusing in particular on the period between 4-10y of age [e.g., @Coley1995; @Erickson2010; @Gutheil1998; @Hatano1994; @Jipson2007; @Medin2010a; @Ochiai1989; @Opfer2004]. This case study has also piqued the interest of computational cognitive scientists, playing a role in the development and refinement of sophisticated computational approaches to modeling human-like conceptual change [e.g., @Rogers2003; @Saxe2013].

Meanwhile, under the unifying label of "theory of mind," thousands of studies have documented major improvements over the course of early and middle childhood in children’s abilities to take others’ perspectives, predict and explain people’s emotions, represent false beliefs, and integrate representations of beliefs and intentions in evaluating moral responsibility [for reviews, see @Flavell1999; @Gelman1981a; @Gelman1983; @Wellman2015]. A search of the PsycInfo database for publications with the phrase "theory of mind" in the title yields well over 2000 results as of August 2019; a full review of these findings is far beyond the scope of this dissertation. Suffice it to say that these studies offer overwhelming evidence that becoming a sophisticated reasoner—and particularly a sophisticated social reasoner—requires substantial refinement of one’s representations of others’ experiences, abilities, beliefs, desires, and so forth. 

## Open questions

Studies of conceptual change in children's understanding of the mind have generally focused on changes in children's beliefs about the world (e.g., Does the child believe that the moon has intentions?); or on changes in children's intuitive theories (e.g., Does the child draw on social-psychological or biological causes when explaining an entity's behavior? Do they include beliefs, in addition to desires, in their representations of the mental states that drive people's actions?). 

For the most part, however, these studies do not address the structural organization of children's representations of mental life—a key ontological structure underlying these beliefs and intuitive theories. Terms like "intention," "belief," and "desire" abound in the scientific theories reviewed in the previous section—but how well do these terms correspond to children's own understanding of types of mental states (or, for that matter, to that of adults)? How do children conceive of the similarities, distinctions, and logical relations among the wide variety of experiences and abilities that might be considered part of mental life? How might this organizational structure change over development? 

In other words, although the field of developmental psychology has made great progress investigating changes in children's beliefs and intuitive theories about the mind, we have very little understanding of changes in _conceptual structure_ in this domain. (See @Chi2009; and @Keil2009; for extended discussions of different kinds of conceptual change.)

Questions about the parts and structure of the mind have their roots in antiquity; I return to parallels between the current work and these ancient lines of inquiry at the end of this chapter. First, however, I describe and reflect on a modern approach to investigating the structural organization of _adults'_ representations of mental life, pioneered by a team of social psychologists in their work on the "dimensions of mind perception."


# Gray, Gray, and Wegner's [-@Gray2007c] "dimensions of mind perception"

Twelve years ago, a team of social psychologists published a brief but highly impactful paper in the journal _Science_. The paper presented the results of a large-scale study in which adult participants were asked to compare the mental capacities of a variety of target characters, including two human adults, a child, an infant, a fetus, a person in a persistent vegetative state, a dead person, a chimpanzee, a dog, a frog, a robot, God, and themselves. From these assessments, the authors derived two axes of variability in participants' responses: a dimension they called “experience,” which captured the extent to which participants considered a character to be capable of hunger, fear, pain, pleasure, rage, desire, personality, consciousness, pride, embarrassment, and joy; and a dimension they called “agency,” which captured the extent to which participants considered a character to be capable of self-control, morality, memory, emotion recognition, planning, communication, and thought. They called these two dimensions the "dimensions of mind perception" [@Gray2007c].

The idea that attributions of different aspects of mental life might play distinct roles in human reasoning and behavior has captured the interest of psychologists and philosophers alike [see @Epley2010], and the particular dimensions of "experience" and "agency" that Gray et al. described have been invoked to inform such diverse topics as the objectification of women [@Gray2011d]; the dynamics of human–robot interaction [@Brink2017; @Gray2012]; the social–cognitive signatures of autism, psychopathy, and other disorders [@Akechi2018; @Gray2011]; beliefs about supernatural beings [@Heiphetz2018; @Willard2019]; and general theories of moral reasoning [@Gray2012a; @Gray2007c; cf. @Sytsma2012].

Beyond this, Gray et al.'s study was groundbreaking in several more general senses. It was among the first generation of psychological studies to be conducted entirely online, which yielded a dataset including well over 2000 participants—an order of magnitude larger than most samples in psychology at the time. It was ambitious in scope, including questions about such deep and difficult concepts as consciousness, morality, and self-control, applied to such socially charged entities as a human fetus, a person in a persistent vegetative state, a "social robot," and God. It made use of an entirely data-driven (rather than hypothesis-driven) statistical procedure—principal components analysis—which just a decade or so earlier was so prohibitively expensive in terms of time and computational power that hardly any mainstream psychologists knew how to conduct it. In other words, Gray et al. collected big data on a topic at the core of experimental philosophy and analyzed it using an unsupervised learning technique—all before "big data," "experimental philosophy," and "unsupervised learning" became the buzzwords that they are today.

## Critiques

This study was not without its flaws. Critical reflection on Gray et al.'s [-@Gray2007c] methods was a major motivation for the studies of adults included in this dissertation [Studies 1a-1d, first published in @Weisman2017c]. I describe these critiques in detail here in the spirit of seeking to deepen the field's understanding of their findings, and as a foundation for my own work, which was designed and executed with these critiques in mind.[^1]

[^1]: Special thanks to Heather M. Gray for providing materials and further details about the implementation of the original study.

First, let us revisit Gray et al.'s study from the perspective of the participant, starting in the moments before data collection even began. Upon arrival to the website hosting the study, participants were told about the purpose of the study and introduced to the thirteen target characters whose minds they would be asked to consider. Photographs of target characters were presented alongside verbal descriptions that varied in their richness and detail (e.g., "Nicholas is a five-month-old baby" vs. "The Green Frog can be found throughout eastern North America. This classic 'pond frog' is medium-sized and green or bronze in color. Daily life includes seeking out permanent ponds or slow streams with plenty of vegetation"). Sometimes these descriptions included information about the correct way to assess certain mental capacities (e.g., "Gerald [the patient in a persistent vegetative state] _does not appear to communicate with others or make purposeful movements_"; "Many people believe that God is _the creator_ of the universe and the _ultimate source of knowledge, power, and love_"; emphasis added), or featured anthropomorphic language—such as personal pronouns and names—that may have biased participants' construals of more controversial entities [e.g., "_Toby_ is a two-year-old wild chimpanzee"; _Kismet_ [the 'social robot'] perceives a variety of natural social signals from sound and sight, and delivers _his_ own signals back to the human partner..."; emphasis added; @Gray2007c].

Participants were then asked to choose which condition they would like to participate in [e.g., choosing a survey that was described as asking them "to judge which character is more capable of experiencing physical or emotional pain" vs. one that was described as asking them "to judge which character is more capable of telling right from wrong and trying to do the right thing"; @Gray2007c]. Participants could opt to participate in as many of these conditions as they liked, in whatever order they chose. This could well have introduced bias into participants' responses (e.g., if participants who were more interested in moral philosophy were more likely to opt into the morality condition than the pain condition, or if participants disproportionately chose to complete the pain condition directly before the morality condition). 

At this point, the study began in earnest. Each participant engaged in a series of comparisons between pairs of target characters, focusing on a single mental capacity for the duration of the survey. For example, a participant who chose the morality survey would  proceed through all possible pairings of the 13 target characters, for a total of 78 trials per survey; on each trial the participant would answer the question "Which character do you think is more capable of telling right from wrong and trying to do the right thing?" on a five-point scale from "much more [character A]" to "much more [character B]." Reflecting on this experience from the perspective of the participant, I have come to believe that this procedure did not actually assess people’s intuitions about the similarities and differences _among mental capacities_, but rather their intuitions about the similarities and differences _among social beings_. The explicit task for the participant, both within each trial and across trials, was to compare and contrast target characters. Only the minority of participants who opted to participate in more than one condition were asked to consider the similarities and differences across mental capacities—and even then, they likely assessed only a few capacities, and only in the context of in long experimental "blocks" of 78 trials per capacity. As I have argued elsewhere, this procedure likely encouraged participants to think about the similarities and differences among the target characters: What do characters have in common, and how do they differ? Conversely, assessing people’s intuitions about the structure of mental life requires a sensitive measure that encourages participants to think about the connections and divisions among mental capacities themselves: Which capacities "go together," and which capacities are more distinct? [See @Weisman2017c.]

Aside from these critiques of the methods employed in Gray et al.'s [-@Gray2007c] study, their unusual analysis approach also bears critical reconsideration. 2399 completed surveys were included in the dataset, each of which consisted of questions about a single mental capacity for every possible pair of target characters (for a total of 78 datapoints per survey). Before conducting principal components analysis, however, this very large dataset was reduced to a much smaller set of summary scores on each mental capacity for each character. Translating the paired comparisons into summary scores necessitated the unconventional approach of averaging across all of the comparisons involving that character (i.e., treating a rating of "much more [character A]" as an absolute measure of character A's capacity, regardless of whether character A was compared to character B or character C) and reusing the same data to calculate summary scores for other characters. This process yielded a summary dataset consisting of "mean relative ratings" for 18 mental capacities for each of the 13 target characters—an extremely small dataset to enter into a dimensionality reduction technique like principal components analysis. Moreover, this summary dataset was of an inappropriate "shape" for this approach, featuring fewer "subjects" (13 target characters) than "items" (18 mental capacities); for comparison, best practices for this kind of dimensionality reduction commonly specify a subject-to-item ratio of 5:1 or even 10:1 [e.g., @Costello2005]. In principle, one of the consequences of such a small subject-to-item ratio would be to constrain the possible outcomes of the analysis, rendering it very unlikely to detect more than one or two "dimensions." Indeed, the authors' interpretation of their results neglected to account for the fact that the first of these dimensions (what they termed "experience") accounted for fully 88% of the variance in characters' mean mental capacity scores, which calls into question whether this analysis detected any meaningful multi-dimensional structure in the first place.

## Contributions

Despite what I perceive to be substantial flaws in this particular study, I continue to consider Gray et al.'s work to be a major inspiration for my own. I will conclude this section by highlighting three aspects of this work that I adopted (and attempted to expand and improve upon) in the studies included in this dissertation.

First, _a description of "mind" as a multidimensional construct_. Perhaps the most radical—and, I would argue, under-valued—contribution of Gray et al.'s work on mind perception was the very premise of their study: that people's understanding of mental life might be structured along multiple, meaningful "dimensions." Gray et al.'s study identified a level of conceptual organization intermediate between the broad concept of "mind" and the narrow definitions of individual mental states (e.g., "joy," "vision," "belief," "desire"). In so doing, it introduced the idea—absent from the majority of relevant work in developmental psychology, as I argued earlier—that such a conceptual organization might exist, that it can be identified empirically, and that it is worth studying. Most of the subsequent work stemming from Gray et al.'s findings has focused on the potential social and moral ramifications of the experience-agency framework [e.g., @Akechi2018; @Brink2017; @Gray2011d; @Gray2012; @Gray2012a; @Gray2011; @Heiphetz2018; @Sytsma2012; @Willard2019]. I would like to draw attention to the fact, however, that the original study actually attempted to describe the structure organization of representations of mental life _before_ turning to these social behavioral implications. In my view, articulating this ontological question and attempting to answer it empirically stands as a key contribution to the field, regardless of my critiques of the design and analysis of this particular study.

Second, _an expansive view of mental life_. Gray et al. included an unprecedentedly wide variety of "mental capacities" in their study—not only the cognitive and emotional abilities that are commonly targeted in studies of reasoning about mental states, but also less common examples of mental states, such as physiological sensations and capacities for emotion recognition and moral reasoning. In my view, this expansive scope is critical for getting a holistic sense of this complicated domain. 

Third—and perhaps most critically—*a bottom-up approach*. Gray et al. [-@Gray2007c] did not generate a theory of "dimensions of mind perception" a priori and set out to confirm or disconfirm this theory; neither did they ask participants to articulate their own conceptualization of this domain. Instead, they relied on an unsupervised learning algorithm to reconstruct participants' representations of a conceptual domain "from the bottom up." [See also @Haslam2008, for a similar bottom-up approach to identifying which aspects of mental life might be considered central to "human nature," and which might be considered "uniquely human."] Such data-driven approaches have become more and more popular in social psychology, particularly as statistical computing software becomes faster and more accessible. Although this work is rarely portrayed as bearing on such "cognitive" topics as conceptual representations, I believe that such bottom-up approaches have tremendous potential to advance our understanding of conceptual representations of mental life and their development over childhood.

One of the primary advantages of such a bottom-up approach, in my view, is its potential to elucidate the kinds of deep conceptual structures that are difficult for participants to report on directly. Gray et al.'s particular implementation of this bottom-up approach is especially compelling to me as a developmental psychologist because of its simplicity. Their empirical paradigm rests on the premise that complex conceptual structures can be uncovered from participants’ answers to relatively simple, concrete questions drawing on participants' knowledge or intuitions about familiar entities in the world. This style of questioning lends itself naturally to adaptation for young children.

Another major advantage of a bottom-up approach is that the conceptual structures it reveals can, in principle, differ dramatically from the assumptions of a research team. These are especially compelling advantages in the domain of conceptual _change_—in which, by definition, participants struggle to introspect and articulate their reasoning, and findings often conflict with adult intuitions (including the intuitions of adult researchers). In contrast to a top-down approach, in which the researcher must anticipate in advance one or more alternatives forms that this representation must take—and, if they are interested in its development, one or more dimensions along which this representation might vary over childhood—a bottom-up approach allows structures, and changes in these structures, to emerge organically, and to vary along both anticipated and unanticipated axes of comparison.


# Promising precursors to using a bottom-up approach with children

To my knowledge, there have been only a few attempts to employ a bottom-up approach to study representations of mental life among children. First, in a series of studies with 8- to 11-year-old children, Fabricius, Schwanenflugel, and colleagues explored one corner of this conceptual space, focusing on how children come to distinguish among different “ways of knowing.” In a representative study, 8- and 10-year-old children and adults rated the similarity of pairs of activities that involved various kinds of cognitive abilities [e.g., “Making a list at home of all the kids in your new class without missing any”; “Trying to find the North Star in the sky on a starry night”; @Fabricius1989]. Their results suggested that children gradually come to distinguish between more “perceptual” aspects of knowing (e.g., seeing, hearing) vs. more “conceptual” aspects of knowing (reasoning, understanding) at some point in middle childhood, only coming to represent ways of knowing along a second axis, how much they rely on “memory,” later in adolescence [@Fabricius1989; @Schwanenflugel1999; @Schwanenflugel1994a; @Schwanenflugel1994; @Schwanenflugel1996a. (See also @Rips1989 for a related pair of studies focused on adults' representations of what they termed "mental activities," including thinking, reasoning, and problem-solving; and @Hoskens1991 for work on adults' representations of "intelligence-related" mental capacities.)

More recently, Nook and colleagues have explored another important aspect of children’s representations of mental life: their developing understanding of emotions. In their study, participants between the ages of 6 and 25 years rated the similarity of pairs of emotion words (e.g., “happy” vs. “angry”); these similarity ratings suggested that younger children first represent emotions along a one-dimensional space (positive vs. negative valence), before gradually coming to represent emotions along a second dimension (high vs. low arousal) over the course of later childhood and adolescence [@Nook2017e]. 

Both of these fascinating results suggest that the conceptual organizations of "cognitive" and "emotional" states are revised and refined over development, in processes that extend well into middle childhood (and beyond)—but neither of these studies took the more expansive outlook of Gray et al. [-@Gray2007c] that I believe is critical for understanding this complex domain of human reasoning.


# The current project

In this dissertation I unite the structural orientation, bottom-up approach, and sweeping scope provided by Gray et al.'s [-@Gray2007c] work on the "dimensions of mind perception" with the traditions of work from developmental psychology on the animate-inanimate distinction, lay biology and psychology, and theory of mind. My goal is to characterize the development of conceptual representations of mental life in the modern US context.

## Three key questions, inspired by the ancients

In describing the theoretical roots of this project, I have focused on empirical studies from developmental and social psychology—but human inquiry into the nature of the mind is much older than the field of psychology. Interest in the nature and structure of the mind (often referred to as the "soul" or "psyche") extends back to the philosophers and spiritual leaders of antiquity, including extensive treatments of this topic by Socrates, by way of Plato; Aristotle; and the Buddha; among many others. A comprehensive analysis of these philosophical theories is beyond the scope of the current dissertation. 

Importantly, what I pursue in my empirical work is not the _true_ nature of mental life, but ordinary people's _perceptions_ of its nature (what I refer to as their "conceptual representations"). I am indebted to these ancient philosophers, however, for a certain ontological bent toward this topic—which I think is worth spelling out here, because it differs in certain respects from mainstream approaches to conceptual representations in the modern empirical study of cognitive development. I have structured my exploration of conceptual representations of mental life around three deeply related questions: 

1. What are the components, or "conceptual units," that anchor representations of mental life at different points in development?
2. How are these conceptual units organized in relation to each other, and how does this organization change over development?
3. How do people of different ages deploy their conceptual representations of mental life to reason about specific entities in the world—namely, animate beings vs. inanimate objects?

As it turns out, each of these questions parallels a key aspect of ancient philosophical inquiries into the nature of the mind (though I did not have such a lofty goal in mind at the outset of this work). 

Plato, for example, describes a theory of the _psyche_ (typically translated as "soul") that addresses (1) the parts of the soul (reason, spirit, and appetite); (2) the hierarchical relationships among these parts (reason as "the charioteer," whose role is to drive two "horses" which tend to pull in opposite directions: spirit and appetite); and (3) the way this structure can be useful in making sense of social life (e.g., in identifying classes of people who are ruled primarily by reason, spirit, or appetite). [See @Brown2017 for a comprehensive summary and discussion.]

In a close parallel, Aristotle's _De Anima_ also presents a theory of the soul (_psyche_ in Greek; _anima_ in Latin) that addresses (1) the distinct faculties of the soul (nutrition, perception, reason, and perhaps desire); (2) the hierarchical relationships among these faculties (the presence of reason in an entity implies the presence of perception and nutrition, but the reverse is not true; likewise, the presence of perception implies the presence of nutrition, but the reverse is not true); and (3) the way this structure makes sense of the variety of beings in the world (plants have only a nutritive soul; non-animals have both nutritive and perceptual souls; and only humans have nutritive, perceptual, and intellectual souls). [See @Shields2016 for a comprehensive summary and discussion.]

The Buddha—a rough contemporary of Aristotle, located half a world a way and emerging from a very different cultural context and historical tradition—also appears to have touched on these three questions in his teachings on sentience, addressing (1) the aggregates (_skandha_) that compose sentient beings (material form, feelings, perceptions or thoughts, impulses or dispositions, and consciousness); (2) the ever-changing relationships among these components (particularly the fact that their aggregation in an individual sentient being is temporary and in some ways illusory); and (3) the way this structure impacts everyday life (namely, by distinguishing sentient beings from the non-sentient world, and binding sentient beings to a cycle of suffering). [See @emmanuel2015companion for extended summary and discussion of relevant topics in Buddhist philosophy.]

Of course, both the content of these ancient theories and the modes of inquiry these thinkers employed differ dramatically from what we would recognize as theories of "the mind" in twenty-first century psychological science. But I have found their shared, three-pronged ontological approach—anchored by the basic questions _What are the units?_, _What are the relationships among them?_ and _How are these structures deployed?_—to be extremely useful in my exploration of ordinary people's understanding of the mind in the modern US context. These three questions form the backbone of this dissertation.


## Overview of the dissertation

The remainder of this dissertation is devoted to describing a series of empirical studies that shed new light on these three key questions about conceptual representations of mental life. I begin by identifying "conceptual units" at three points in development in the modern US context: early childhood (4-6y), middle childhood (7-9y), and adulthood (Chapter III). Next, I explore the relationships among these conceptual units, and how these relationships might evolve and change over this period of development (Chapter IV). I then consider the deployment of these conceptual representations in one aspect of social reasoning, using the apparent conceptual structure established in Chapters III-IV to shed light on children's developing mental capacity attributions to animate beings vs. inanimate objects (Chapter V). Finally, I synthesize my findings from these three lines of inquiry and step back to reflect on how these three aspects of conceptual development might be related to one another, what this case study of representations of mental life might reveal about conceptual development more broadly, and the potential consequences of these representations of mental life in children's social development (Chapter VI). 

First, in Chapter II, I provide an overview of my general empirical approach and the specific methods I employed in the four large-scale studies included in this dissertation.


# References
