---
title: "Chapter I: Theoretical foundations"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes

# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

The act of attributing mental life to other beings in the world is a fundamental part of human experience: From early in life, we look at others around us and see not just physical objects, but people, minds, with sensations, emotions, thoughts, and memories of their own. Viewing others in this way lays the foundation for our social lives and our behavior toward others. We might infer our friends’ goals and try to help, or identify things that others have forgotten or misunderstood and correct them; we delight in each other’s happiness, seek comfort from each other in times of sadness, and plan our actions to avoid (or to appear to avoid) causing others emotional or physical pain. In this sense, representations of mental life are at the core of human social life.

But mental life is complex, encompassing a wide range of experiences and abilities that stand in complicated relationships to each other and play a wide range of roles in the behaviors of and interactions between social beings. Capacities for perception, beliefs, desires, goals, thoughts, emotions, physiological sensations, and other mental states have some things in common—e.g., these mental states are commonly experienced as occurring privately "inside" an individual, without being directly accessible to anyone else (although they might facial expressions, words, actions, and other publicly observable behaviors)—but mental states also differ along many dimensions. Some mental states are closely related to specific bodily organs (e.g., people see things with their eyes, feel hunger in their stomachs), and others less obviously so (where do people experience belief?). Some are positively or negatively valenced (e.g., pain feels bad, happiness feels good), others are more neutral, or vary in valence depending on the circumstance (thought, olfaction). Some mental states involve taking in information about the environment (e.g., seeing, hearing), while others involve storing or updating that information (remembering, learning), or using it to bring about changes in the external world (planning, making choices). In a given social context, certain mental states might be considered more appropriate or socially productive than others (e.g., love vs. anger, guilt vs. pride, excitement vs. contentment (XX CITE TSAI on ideal affect). And people might believe that certain mental capacities are shared by a wide range of entities (e.g., even insects might experience some kind of hunger; even robots might have a capacity for "memory," in some sense), while others are limited to a smaller subset of beings (perhaps only humans experience embarrassment; XX CITE HASLAM 2008).

This makes conceptual representations of mental life a fascinating case study of abstract reasoning and its development: How do people come to represent this complex conceptual space? This question has deep roots in cognitive and developmental psychology—but in attempting to address it, I draw inspiration from both modern social psychologists and ancient philosophers. In the following sections, I discuss the theoretical foundations of my approach, beginning with a groundbreaking study in social psychology.


# Theoretical foundations

## Recent work in social psychology on the "dimensions of mind perception"

A little over 10 years ago, a team of social psychologists published a brief but groundbreaking paper in the journal _Science_. The paper presented the results of a pioneering study in which adult participants were asked to compare the mental capacities of a variety of humans, animals, and other target characters. From these assessments, the authors derived two axes of variability in participants' responses: a dimension they called “experience,” which captured the extent to which participants considered a character to be capable of hunger, fear, pain, pleasure, rage, desire, personality, consciousness, pride, embarrassment, and joy; and a dimension they called “agency,” which captured the extent to which participants considered a character is capable of self-control, morality, memory, emotion recognition, planning, communication, and thought. They called these two dimensions the "dimensions of mind perception" (XX CITE GRAY).

This study was ground-breaking in several ways: It was among the first generation of psychological studies to be conducted entirely online, which had allowed the authors to collect dataset including well over 2000 participants—at least an order of magnitude larger than most samples in psychology at the time. It was ambitious in scope, including questions about such deep and difficult concepts as consciousness, morality, and self-control, applied to such socially charged entities as a human fetus, a person in a persistant vegetative state, a "social robot," and God. It made use of an entirely data-driven (rather than hypothesis-driven) statistical procedure—principal components analysis—which just a decade or so earlier was so prohibitively expensive in terms of time and computational power that hardly any mainstream psychologists knew how conduct it. In other words, Gray et al. collected big data on a topic at the core of experimental philosophy and analyzed it using an unsupervised learning technique—all before "big data," "experimental philosophy," and "unsupervised learning" became the keywords that they are today. It was a groundbreaking piece of work, truly ahead of its time.

Of course, this single study was not without its flaws. Participants were allowed to choose which condition they participated in (e.g., choosing a survey that was described as asking them "to judge which character is more capable of experiencing physical or emotional pain" vs. one that was described as asking them "to judge which character is more capable of telling right from wrong and trying to do the right thing"; XX CITE GRAY SOM), and could opt to participate in as many of these conditions as they liked, in whatever order they chose—all of which could have introduced bias into participants' responses (e.g., if participants who were more interested in moral philosophy were more likely to opt into the "morality" condition). The target characters were presented alongside verbal descriptions that varied in their richness and detail (e.g., "Nicholas is a five-month-old baby" vs. "The Green Frog can be found throughout eastern North America. This classic 'pond frog' is medium-sized and green or bronze in color. Daily life includes seeking out permanent ponds or slow streams with plenty of vegetation"), and which sometimes included information about the correct way to assess to certain mental capacities (e.g., "Gerald [the patient in a persistant vegetative state] _does not appear to communicate with others or make purposeful movements_"; emphasis added) or anthropomorphic language—such as personal pronouns and names—that may have biased participants' construals of more controverisal entities (e.g., "_Toby_ is a two-year-old wild chimpanzee"; _Kismet_ [the 'social robot'] perceives a variety of natural social signals from sound and sight, and delivers _his_ own signals back to the human partner..."; emphasis added; XX CITE GRAY SOM). The data-processing pipeline involved using a very large dataset (2399 completed survey, each of which included 78 paired-comparison questions about the relative mental capacities of different characters, for a total of `r 2399 * 78` datapoints) to construct a much smaller dataset (13 target characters, each associated with a mean relative score for 18 mental capacities, for a total of `r 13 * 18` datapoints) before conducting principal components analysis, which (in principle) constrained the possible outcomes of the analysis—including rendering it extremely unlikely to detect more than one or two "dimension." The interpretation of this analysis neglected to account for the fact that the first of these "dimensions" (experience) accounted for fully 88% of the variance in characters' mean mental capacity scores, which calls into question whether this analysis detected any meaningful multi-dimensional structure in the first place.

Aside from these critiques, upon deeper reflection on the details of the methods employed in Gray et al.'s work—in which each participant engaged in a series of paired comparisons between different target characters while focusing on a single mental capacity for the duration of the survey—I came to believe that this study did not actually assess people’s intuitions about the similarities and differences _among mental capacities_, but rather their intuitions about the similarities and differences _among social beings_. In the original publication of the first set of studies included in this dissertation (referred to here as Studies 1a-1d),
my co-authors and I argued that assessing people’s intuitions about the structure of mental life requires a sensitive measure that encourages participants to think about the connections and divisions among mental capacities themselves: Which capacities "go together," and which capacities are more distinct? (See XX CITE WEISMAN et al., 2017).

Despite what I perceive to be substantial flaws in this particular study, I continue to consider Gray et al.'s work to be a major inspiration for my own. Although this work is not typically described as an attempt to elucidate "conceptual structure" or "mental representations," I believe this kind of approach has tremendous potential to advance our understanding of conceptual representations of mental life—and their development over childhood. I will conclude this section by highlighting two aspects of this work that I adopted (and attempted to expand and improve upon) in the studies included in this dissertation.

First, _an expansive view of mental life_. Rather than focusing on beliefs and understanding within particular domains, such as "cognition" (e.g., XX CITE SCHWANENFLFUGEL, XX CITE RIPS & CONRAD 1989) or "emotion" (XX CITE NOOK 2017; see the following section for further discussion of these two lines of work), Gray et al. included an unprecedentedly wide variety of "mental capacities" in their study—from physiological sensations like hunger and pain, to capacities for emotion recognition and moral reasoning (among many others). In my view, this expansive scope is critical for getting a holistic sense of this complicated domain. In the current studies, I begin with an even more expansive view of the particular capacities that might be included in people's conceptual represnetations of mental life, in an attempt to attain an even more holistic perspective on this complex domain.

Second, _a bottom-up approach_. Gray et al. (XX CITE GRAY 2007) did not generate a theory of "dimensions of mind perception" a priori and set out to confirm or disconfirm this theory; neither did they ask participants to articulate their own conceptualization of this domain. Instead, they relied on an unsupervised learning algorithm to reconstruct participants' representations of a conceptual domain "from the bottom up." (See also XX HASLAM 2008, for a similar bottom-up approach to identifying which aspects of mental life might be considered central to "human nature," and which might be considered "uniquely human.") Such data-driven approaches have become more and more popular in social psychology, particularly as statistical computing software becomes faster and more accessible. Although this work is rarely portrayed as bearing on such "cognitive" topics as conceptual representations, I believe that such bottom-up approaches have tremendous potential to advance our understanding of conceptual representations of mental life and their development over childhood.

One of the primary advantages of such a bottom-up approach, in my view, is its potential to elucidate the kinds of deep conceptual structures that are difficult for participants to report on directly. Gray et al.'s particular implementation of this bottom-up approach is particularly compelling to me as a developmental psychologist because of its simplicity. Their empirical paradigm rests on the premise that complex conceptual structures can be uncovered from participants’ answers to relatively simple, concrete questions drawing on participants' knowledge or intuitions about familiar entities in the world (e.g., “Which character do you think is more capable of feeling joy: a green frog, or an adult woman?"). This style of questioning lends itself naturally to adaptation for young children.

Another major advantage of a bottom-up approach is that the conceptual structures it reveals can, in principle, differ dramatically from the assumptions of a research team. These are especialaly compelling advantages in the domain of conceptual _change_—in which, by definition, participants struggle to introspect and articulate their reasoning, and findings often conflict with adult intuitions. In contrast to a top-down approach, in which the researcher must anticipate in advance one or more alternatives forms that this representation must take—and, if they are interested in its development, one or more dimensions along which this representation might vary over childhood—a bottom-up approach allows structures, and changes in these structures, to emerge organically, and to vary along both anticipated and unanticipated axes of comparison.

## Rich traditions in cognitive and developmental psychology

Prior to the surge of interest in "mind perception" that Gray et al.'s (XX CITE GRAY 2007) groundbreaking study inspired, investigations of how ordinary people conceptualize "the mind" were more often in the purvue of cognitive and developmental psychology. 

In particular, decades of work on cognitive development have made it clear that early and middle childhood (roughly, from the ages of 4 years to 10 years of age) is a time of rapid change in children’s understanding of the vast range of experiences and abilities that might be considered part of “mental life.” Under the unifying labels of "lay psychology" and "theory of mind," hundreds of studies have documented dramatic shifts in children’s abilities to take others’ perspectives, predict and explain people’s emotions, represent false beliefs, and integrate representations of beliefs and intentions in evaluating moral responsibility (for reviews, see XX CITE FLAVELL, 1999; XX CITE WELLMAN, 2015). The period between 4-10y of age has also been the focus of a rich tradition of work on lay biology extending back nearly a century (e.g., XX CITE CAREY, 1985; XX CITE MEDIN et al., 2010; XX CITE PIAGET, 1929), which has included forays into children’s understanding of which beings in the world are susceptible to physiological sensations like hunger, pain, and fatigue. 

Taken together, this body of work makes the case that becoming a sophisticated reasoner—and particularly a sophisticated social reasoner—requires substantial refinement of one’s representations of others’ experiences, beliefs, desires, and needs—in other words, changes in one’s conceptual representations of mental life. But the vast majority of this work has proceeded by postulating distinct representations of such categories as “perceptions,” “beliefs,” “desires,” and “emotions." Do these categories correspond to children’s own developing understanding of the structure of mental life? How do children conceive of the connections and distinctions among mental states, and how does this conceptual structure shape their understanding of the various humans, animals, technologies, and other “beings” in the world around them?

To my knowledge, there have been only a few attempts to employ a "bottom-up" (as introduced in the previous section) to address these questions among children—but these approaches have been promising. 

In a series of studies with 8- to 11-year-old children, Fabricius, Schwanenflugel, and colleagues explored one corner of this conceptual space, focusing on how children come distinguish among different “ways of knowing.” In a representative study, 8- and 10-year-old children and adults rated the similarity of pairs of activites that involved various kinds of cognitive abilities (e.g., “Making a list at home of all the kids in your new class without missing any”; “Trying to find the North Star in the sky on a starry night”; XX CITE FABRICIUS 1989). Their results suggested that children gradually come to distinguish between more “perceptual” aspects of knowing (e.g., seeing, hearing) vs. more “conceptual” aspects of knowing (reasoning, understanding) at some point in middle childhood, only coming to represent ways of knowing along a second axis, how much they rely on “memory,” later in adolescence (XX CITE FABRICIUS 1989; SCHWANENFLUGEL 1996; SCHWANENFLUGEL 1994; see also XX CITE RIPS & CONRAD, 1989, for a related pair of studies focused on adults' representations of what they termed "mental activities," including thinking, reasoning, and problem-solving). 

More recently, Nook and colleagues have explored another important aspect of children’s representations of mental life: their developing understanding of emotions. In their study, participants between the ages of 6 and 25 years rated the similarity of pairs of emotion words (e.g., “happy” vs. “angry”); these similarity ratings suggested that younger children first represent emotions along a one-dimensional space (positive vs. negative valence), before gradually coming to represent emotions along a second dimension (high vs. low arousal) over the course of later childhood and adolesence (XX CITE NOOK 2017). 

Both of these fascinating results suggest that children are revising and refining their understanding of cogntion and emotion well into middle childhood (and beyond)—but neither of these studies took the more expansive outlook of Gray et al. (XX CITE GRAY 2007) that I believe is critical for understanding this complex domain of human reasoning.


# The current project: Exploring development in three aspects of conceptual representations of mental life

My goal in this dissertation is to characterize the development of conceptual representations of mental life in the modern US context. I aim to unite the "bottom-up" approach and sweeping scope provided by recent work in social psychology with the framework of "lay concepts" and "folk theories" that has emerged from cognitive and developmental psychology over the past several decades (both reviewed in the previous section). In addition to providing a case study of abstract reasoning and its development, I believe this work has the potential to shed new light on the development of the animate-inanimate distinction—a topic with a rich history in psychology extending back to Piaget. 

Indeed, the roots of this topic are even older than the field of psychology itself; interest in the nature of the mind (often referred to as the "soul" or "psyche") extends back to the philosophers and spiritual leaders of antiquity, including extensive treatments of this topic by Socrates, by way of Plato (XX CITE REPUBLIC; XX CITE PHAEDRUS); Aristotle (XX CITE DE ANIMA); and the Buddha (XX CITE FIVE AGGREGATES); among many others. A comprehensive analysis of these philosophical theories is beyond the scope of the current dissertation—and, of course, what I pursue in my empirical work is not the _true_ nature of mental life, but ordinary people's _perceptions_ of its nature (what I refer to as their "conceptual representations"). 

I am indebted to these ancient philosophers, however, for a certain ontological bent toward this topic—which I think is worth spelling out here, because it differs in certain respects from mainstream approaches to conceptual representations in the modern empirical study of cognitive development. I have structured my exploration of conceptual representations around mental life around three deeply related questions: 

1. What are the components, or "conceptual units," that anchor representations of mental life at different points in development?
2. How are these conceptual units organized in relation to each other, and how does this organization change over development?
3. How do people of different ages deploy their conceptual representations of mental life to reason about specific entities in the world—namely, animate beings vs. inanimate objects?

As it turns out, each of these questions parallels a key aspect of ancient philosophical inquiries into the nature of the mind (though I did not have such a lofty goal in mind at the outset of this work). Plato, for example, describes a theory of the _psyche_ (typically translated as "soul"—an entity that encompasses most of what I refer to here as "mental life") that addresses (1) the parts of the soul (reason, spirit, and appetite); (2) the hierarchical relationships among these parts (reason as "the charioteer," whose role is to drive two "horses" which tend to pull in opposite directions: spirit and appetite); and (3) the way this structure can be useful in making sense of social life (e.g., in identifying classes of people who are ruled primarily by reason, spirit, or appetite; see XX CITE SEP ENTRY ON "Plato’s Ethics and Politics in The Republic" for a comprehensive summary and discussion). In a close parallel, Aristotle's _De Anima_ also presents a theory of the soul (_psyche_ in Greek; _anima_ in Latin) that addresses (1) the distinct faculties of the soul (nutrition, perception, reason, and perhaps desire); (2) the hierarchical relationships among these faculties (the presence of reason implies the presence of perception and nutrition, but the reverse is not true; likewise, the presence of perception implies the presence of nutrition, but he reverse is not true); and (3) the way this structure makes sense of the variety of beings in the world (plants only have a nutritive soul; non-animals have both nutritive and perceptual souls; and only human have nutritive, perceptual, and intellectual souls) ; see XX CITE SEP ENTRY ON "Aristotle's philosophy" for a comprehensive summary and discussion). Even the Buddha—a rough contemporary of Aristotle, located half a world a way and emerging from a very different cultural and historical context—appears to have touched on these three questions in his teachings on sentience, addressing (1) the aggregates (_skandha_) that compose sentient beings (material form, feelings, perceptions or thoughts, impulses or dispositions, and consciousness); (2) the ever-changing relationships among these components (and particularly the fact that their aggregation in an individual sentient being is temporary and in some ways illusory); and (3) the way this structure impacts everyday life (namely, by distinguishing sentient beings from the non-sentient world, and binding sentient beings to a cycle of suffering; see XX FIND CITATION for a comprehensive summary and discussion).

Of course, both the content of these ancient theories and the modes of inquiry these thinkers employed differ dramatically from what we would recognize as theories of "the mind" in twenty-first century psychological science. But I have found their shared, three-pronged ontological approach—anchored by the basic questions _What are the units?_, _How are they structured?_ and _How are these structures deployed?_—to be extremely useful in my exploration of ordinary people's understanding of the mind in the modern US context, and I suspect they would be well-suited for similar explorations of other conceptual domains (I pick up on this point in Chapter VI). These three questions form the backbone of this dissertation.


# Overview

The remainder of this dissertation is devoted to describing a series of empirical studies that shed new light on these three key questions about conceptual representations of mental life. I begin by identifying "conceptual units" at three points in development in the modern US context: early childhood (4-6y), middle chidlhood (7-9y), and adulthood (Chapter III). Next, I explore the relationships among these conceptual units, and how these relationships might evolve and change over this period of development (Chapter IV). I then consider the deployment or application of these conceptual representations in one aspect of social reasoning, using the apparent conceptual structure established in Chapters III-IV to shed light on children's developing mental capacity attributions to animate beings vs. inaimate objects (Chatper V). Finally, I synthesize my findings from these three lines of inquiry and step back to reflect on how these three aspects of conceptual development might be related to one other, what this case study of representations of mental life might reveal about conceptual development more broadly, and the potential consequences of these representations of mental life in children's social development (Chapter VI). 

First, in Chapter II, I provide an overview of my general empirical approach and the specific methods I employed in the four large-scale studies included in this dissertation.

