---
title: "Chapter III: Changes in conceptual units"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes
   
# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

```{r}
# supporting functions
source("./scripts/max_factors_efa.R")
source("./scripts/reten_fun.R")
source("./scripts/plot_fun.R")
source("./scripts/efa_fun.R")
source("./scripts/ms_fun.R")

# data scripts
source("./scripts/data_s2_ad.R")
source("./scripts/data_s2_79.R")
source("./scripts/data_s3_ad.R")
source("./scripts/data_s3_79.R")
source("./scripts/data_s3_46.R")
source("./scripts/data_s4_ad.R")
source("./scripts/data_s4_46.R")
```

```{r}

```


# Chapter overview

In this chapter, I focus on the first of my three key questions about the development of representations of mental life introduced in Chapter I: _What are the components, or "conceptual units," that anchor representations of mental life at different points in development?_ As described in Chapter II, to address this question I draw on data from all of the current studies (Studies 1-4); for details about the methods of these studies, see Chapter II. The goal of this chapter is to provide "snapshots" of the sets of conceptual units available to participants in early childhood, middle childhood, and adulthood. I note that this was the primary planned analysis for all of the studies included in this dissertation (see, e.g., Weisman et al., 2017). 


# General analysis plan: Identifying conceptual units

In analyzing these datasets with an eye toward identifying "conceptual units," the basic insight is that tracking the covariance of mental capacity attributions provides a way of discovering suites of mental capacities that "hang together" in reasoning about mental life, and that these suites of mental capacities might correspond to the units of some larger conceptual representation of this general domain. To borrow an example from Chapter II: If participants who endorse Capacity X also tend to endorse Capacities Y and Z, this provides some evidence that Capacities X, Y, and Z consitute a suite of mental capacities that are closely associated with the same underlying "conceptual unit." 

One way of restating the general intuition just described would be to say that the goal of the analyses under discussion in this chapter is to uncover a set of latent constructs—"conceptual units"—that could have given rise to the correlations among mental capacity attributions as observed in a given group of participants. A canonical way to accomplish this goal of identifying latent constructs through observed correlations is exploratory factor analysis (EFA), a form of dimensionality reduction that posits that the observed variables in a given dataset are related, to varying degrees, to a smaller set of unobserved "factors"; and that individual observations of each of these variables reflect a combination of the state of these latent factors, a particular variable's relationship to each of these latent factors, and noise. Following this logic, I posit that, for any of the current datasets, the various mental capacities included in that dataset are related, to varying degrees, to a smaller set of latent "conceptual units"; and that a participant's attributions of each of these mental capacities to a particular target character reflects a combination of that participant's beliefs about the extent to which these conceptual units apply to that target character, a particular mental capacity's relationships to each of these conceptual units, and noise. In other words, one way to identify conceptual units for a particular sample of interest (e.g., US adults; US 7- to 9-year-olds) is to conduct an EFA over participants mental capacity attributions and treat the resulting "factors" as candidate conceptual units.

In the remainder of this chapter, I report EFAs for each age group included in each of the current studies (Studies 1-4). For all EFAs, I used ordinary least squares to find the minimum residual solution, using the "psych" package for R (Revelle, 2018). Here I focus on results using Pearson correlations using pairwise complete observations. (In principle, polychoric correlations are better suited to handle responses on a three-point scale; however, doing these analyses with polychoric correlations instead of Pearson correlations generally appeared to over-fit the data, e.g., suggesting retaining many factors that each accounted for only a very small amount of the shared variance. [XX SEE APPENDIX?])

In order to determine how many factors to retain, I examined the results of three factor retention protocols: (1) Parallel Analysis, which compares the observed correlation structure to the correlation structure arising from random datasets of the same size; (2) Minimizing the Bayesian Information Criterion (BIC), which is one method of optimizing both goodness of fit and parsimony; and (3) A set of factor retention criteria that I have used previous work with adults (Weisman et al., 2017), in which I began with the maximal number of factors according to an analysis of degrees of freedom, and retained factors that met all three of the following criteria: (a) had eigenvalues greater than 1.00, (b) individually accounted for greater than 5% of the shared variance before rotation, and (c) were the "dominant" factor (the factor with the strongest absolute factor loading) for at least 1 mental capacity after rotation. For each study, my interpretation of how best to characterize the dataset (i.e., how many factors I observed) is determined by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol. 

To maximize the interpretability of these factors, I present varimax-rotated solutions, which constrain all factors to be orthogonal. (For solutions using oblique ["oblimin"] rotations, which allow for correlated factors, [XX SEE APPENDIX?].)

For two of the current studies (Study 1c and Study 4), participants assessed two target characaters instead of one. For the purposes of the current analyses, I treat each participant's assessments of each target character as a separate set of observations (as if they came from different participants), in effect doubling the sample size for these studies (but ignoring the within-subject design). ([XX SEE APPENDIX?] for separate EFAs of the participants' responses to the first target character that they were assigned to rate vs. the second character.)


# Study 1: An adult endpoint

## Special notes on data processing and analysis

## Results

## Discussion


# Study 2: Conceptual change between middle childhood (7-9y) and adulthood

## Special notes on data processing and analysis

## Results

## Discussion


# Study 3: Conceptual change over early and middle childhood (4-9y)

## Special notes on data processing and analysis

## Results

## Discussion


# Study 4: A focus on early childhood (4-5y)

## Special notes on data processing and analysis

## Results

## Discussion


# General discussion of conceptual units


# Chapter conclusion








# SCRAPS





Scraps:
- [FOR TRANSITION FROM STUDY 2 TO STUDY 3]: As demonstrated in Study 1, among adults the "edge case" and "diverse characters" variants of the general approach have yielded very similar pictures of conceptual representations (see also XX CITE Weisman et al., 2017). If this three-part conceptual structure is stable and robust by the age of 7-9 years, it should manifest among 7- to 9-year-old children under the same range of conditions that it does among adults. Thus, in Study 3...
- [FOR TRANSITION FROM STUDY 3 to STUDY 4]: For the final set of questions, I aimed to select six clear examples of physiological sensations (_BODY_), social-emotional abilities (_HEART_), and perceptual-cognitive capacities (_MIND_), according to Studies 1-2 and Weisman et al.'s (2017) original studies with US adults. We reasoned that if these carefully selected examples of _BODY_, _HEART_, and _MIND_ still elicited differences in correlational structures between 4- to 5-year-old children and adults, this would be particularly strong evidence of age-related changes in conceptual structure. The final set of _BODY_ items included _feel hungry_, _get thirsty_, _feel sick_, _feel tired_, _get scared_, and _smell things_. _HEART_ items included _love someone_, _hate someone_, _feel happy_, _get sad_, _feel sorry_, and _get lonely_. _MIND_ items included _see_, _hear_, _think_, _remember things_, _know stuff_, and _figure things out_. We ensured that each category included a variety of phrasings (e.g., "_feel_ hungry" vs. "_get_ thirsty"; "remember _things_" vs. "know _stuff_") and valences when appropriate (e.g., happiness vs. sadness); when possible, we aimed to have these aspects of phrasing vary orthogonally with categories, such that "get" and "feel" appeared roughly equally often among the _BODY_ and _HEART_ items, and "things" appeared equally often among the _BODY_ and _MIND_ items. 
