---
title: "Chapter IV: Changes in conceptual units"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes
   
# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

Scraps:
- [FOR TRANSITION FROM STUDY 2 TO STUDY 3]: As demonstrated in Study 1, among adults the "edge case" and "diverse characters" variants of the general approach have yielded very similar pictures of conceptual representations (see also XX CITE Weisman et al., 2017). If this three-part conceptual structure is stable and robust by the age of 7-9 years, it should manifest among 7- to 9-year-old children under the same range of conditions that it does among adults. Thus, in Study 3...
- [FOR TRANSITION FROM STUDY 3 to STUDY 4]: For the final set of questions, I aimed to select six clear examples of physiological sensations (_BODY_), social-emotional abilities (_HEART_), and perceptual-cognitive capacities (_MIND_), according to Studies 1-2 and Weisman et al.'s (2017) original studies with US adults. We reasoned that if these carefully selected examples of _BODY_, _HEART_, and _MIND_ still elicited differences in correlational structures between 4- to 5-year-old children and adults, this would be particularly strong evidence of age-related changes in conceptual structure. The final set of _BODY_ items included _feel hungry_, _get thirsty_, _feel sick_, _feel tired_, _get scared_, and _smell things_. _HEART_ items included _love someone_, _hate someone_, _feel happy_, _get sad_, _feel sorry_, and _get lonely_. _MIND_ items included _see_, _hear_, _think_, _remember things_, _know stuff_, and _figure things out_. We ensured that each category included a variety of phrasings (e.g., "_feel_ hungry" vs. "_get_ thirsty"; "remember _things_" vs. "know _stuff_") and valences when appropriate (e.g., happiness vs. sadness); when possible, we aimed to have these aspects of phrasing vary orthogonally with categories, such that "get" and "feel" appeared roughly equally often among the _BODY_ and _HEART_ items, and "things" appeared equally often among the _BODY_ and _MIND_ items. 
