---
title: "Chapter IV: Changes in organization of conceptual units"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes
   
# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

# Chapter overview


# General analysis plan: Assessing the hierarchical organization of conceptual units


# Study 1: An adult endpoint

## Special notes on data processing and analysis

## Results

## Discussion


# Study 2: Conceptual change between middle childhood (7-9y) and adulthood

## Special notes on data processing and analysis

## Results

## Discussion


# Study 3: Conceptual change over early and middle childhood (4-9y)

## Special notes on data processing and analysis

## Results

## Discussion


# Study 4: A focus on early childhood (4-5y)

## Special notes on data processing and analysis

## Results

## Discussion


# General discussion of the hierarchical organization conceptual units


# Chapter conclusion


