---
title: "Chapter V: Changes in deployment of the concept"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes
   
# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

```{r}
# supporting functions
source("./scripts/max_factors_efa.R")
source("./scripts/reten_fun.R")
source("./scripts/plot_fun.R")
source("./scripts/efa_fun.R")
source("./scripts/ms_fun.R")

# data scripts
source("./scripts/data_s1.R")
source("./scripts/data_s2_ad.R")
source("./scripts/data_s2_79.R")
source("./scripts/data_s3_ad.R")
source("./scripts/data_s3_79.R")
source("./scripts/data_s3_46.R")
source("./scripts/data_s4_ad.R")
source("./scripts/data_s4_46.R")
```

```{r}
# what correlation to use
chosen_cor <- "cor" # REPORTED
# chosen_cor <- "poly" # alternative option

# what rotation to use
chosen_rot <- "varimax" # REPORTED
# chosen_rot <- "oblimin" # alternative option

# what factoring method to use
chosen_fm <- "minres" # REPORTED (minimum residuals)
# chosen_fm <- "ols" # ordinary least squares using empirical first derivative
# chosen_fm <- "wls" # weighted least squares
# chosen_fm <- "gls" # generalized weighted least squares
# chosen_fm <- "pa" # principal factors
# chosen_fm <- "ml" # maximum likelihood
# chosen_fm <- "minchi" # minimize ss-weighted chisq
# chosen_fm <- "minrank" # minimum rank
# chosen_fm <- "old.min" # minres < April 2017
# chosen_fm <- "alpha" # alpha fa (Kaiser & Coffey, 1965)

# what scoring method to use
chosen_scores <- "tenBerge" # REPORTED
# chosen_scores <- "regression" # alternative option
```

# Chapter overview

In this chapter, I focus on the third of my three key questions about the development of representations of mental life introduced in Chapter I: _How do people of different ages deploy their conceptual representations of mental life to reason about specific entities in the world?_ As in Chapters III-IV, to address this question I draw on data from all of the current studies (Studies 1-4); for details about the methods of these studies, see Chapter II. The goal of this chapter is to provide "snapshots" of mental capacity attributions to various target characters in early childhood, middle childhood, and adulthood, and to explore in finer-grained detail changes in children's beliefs about the mental lives of these characters between 4-9y of age, with particular attention to children's assessment of animate vs. inanimate beings.


# General analysis plan

## High-level overview

In analyzing these datasets with an eye toward documenting the application or deployment of the conceptual representations described in Chapters III-IV, the basic insight is that the attribution of specific mental capacities to specific target characters provides evidence of how conceptual representations of mental life are deployed in everyday social cognition. In Chapter II, I illustrated this with the following example: If participants who assess the mental capacities of Characters 1, 2, and 3 share one general pattern of mental capacity attributions, and participants who assess the mental capacities of Characters 4, 5, and 6 share another pattern, this provides some evidence that conceptual representations of mental life might play a role in structuring representations of (and interactions with) different classes of beings in the world. Here I will translate this general intuition into a specific analysis plan to be applied to each of these datasets in turn. 

## Details of analyses

XX

# Study 1: An adult endpoint

In our previously published work on these studies (Weisman et al., 2017), we focused mainly on the "conceptual units" analysis presented in Chapter III; we touched only briefly on which mental capacities were attributd to the various target characters included in this study. Here I re-analyze these data from this new perspective.

## Special notes on data processing and analysis

As noted in Chapter II, in the original analysis of these datasets responses were recoded to run from -3 to +3 before analyses (Weisman et al., 2017); in this dissertation, I maintain the 0-6 coding for comparability to Studies 2-4.

## Results

### Study 1a

In Study 1a, `r nrow(d1a_ad_wide)` US adults each assessed a single target character on 40 mental capacities. This study employed the "edge case" variant of the general approach, with participants randomly assigned to assess either a beetle or a robot. (See Chapter II and Weisman et al., 2017, for detailed methods.)

### Study 1b

Study 1b was a direct replication of Study 1a: `r nrow(d1b_ad_wide)` US adults each assessed a single target character (either a beetle or a robot) on 40 mental capacities. (See Chapter II and Weisman et al., 2017, for detailed methods.)

### Study 1c

In Study 1c, `r nrow(d1c_ad_wide)/2` US adults each assessed two target characters on 40 mental capacities. Like Studies 1a and 1b, this study employed the "edge case" variant of the general approach; but in this study, all participants assessed both of these target characters side by side (with left-right position counterbalaned across participants). (See Chapter II and Weisman et al., 2017, for detailed methods.)

### Study 1d

In Study 1d, `r nrow(d1d_ad_wide)` US adults each assessed a single target character on 40 mental capacities. Unlike Studies 1a-1c, this study employed the "many characters" variant of the general approach, in which participants were randomly assigned to assess one of the following 21 target characters: an adult, a child, an infant, a person in a persistent vegetative state, a fetus, a chimpanzee, an elephant, a dolphin, a bear, a dog, a goat, a mouse, a frog, a blue jay, a fish, a beetle, a microbe, a robot, a computer, a car, or a stapler. (See Chapter II and Weisman et al., 2017, for detailed methods.)

## Discussion


# Study 2: Conceptual change between middle childhood (7-9y) and adulthood

In Study 2, `r nrow(d2_ad_wide)` US adults and `r nrow(d2_79_wide)` US children between the ages of `r summary(d2_79$age)["Min."] %>% round(2)`-`r summary(d2_79$age)["Max."] %>% round(2)` years (median: `r summary(d2_79$age)["Median"] %>% round(2)`y) each assessed a single target character on 40 mental capacities. To make the study appropriate for children in this age range, the wording of some the 40 mental capacities employed in Study 1 was modified to use more age-appropriate vocabulary, and participants responded on a 3-point scale ("no," coded as 0; "kinda," coded as 0.5, "yes," coded as 1). This study employed the "edge case" variant of the general approach, with participants randomly assigned to assess either a beetle or a robot. (See Chapter II for detailed methods.)

## Special notes on data processing and analysis

## Results

### Adults

### Children (7-9y)

## Discussion


# Study 3: Conceptual change over early and middle childhood (4-9y)

In Study 3, `r nrow(d3_ad_wide)` US adults, `r nrow(d3_79_wide)` "older" children (`r summary(d3_79$age)["Min."] %>% round(2)`-`r summary(d3_79$age)["Max."] %>% round(2)` years; median: `r summary(d3_79$age)["Median"] %>% round(2)`y), and `r nrow(d3_46_wide)` "younger" children (`r summary(d3_46$age)["Min."] %>% round(2)`-`r summary(d3_46$age)["Max."] %>% round(2)` years; median: `r summary(d3_46$age)["Median"] %>% round(2)`y) each assessed a single target character on 20 mental capacities. To make the study appropriate for children in this age range, participants assessed a subset of the 40 mental capacities employed in Study 2, chosen to represent the three "conceptual units" revealed by Studies 1-2 (BODY, HEART, and MIND) and to cover a similar range of mental capacities as Studies 1-2. As in Study 2, participants responded on a 3-point scale ("no," coded as 0; "kinda," coded as 0.5, "yes," coded as 1). This study employed the "diverse characters" variant of the general approach, with participants randomly or pseudo-randomly assigned to assess either one of the following 9 characters: an elephant, a goat, a mouse, a bird, a beetle, a teddy bear, a doll, a robot, or a computer. (See Chapter II for detailed methods.)

## Special notes on data processing and analysis

## Results

### Adults

### Children (7-9y)

### Children (4-6y)

## Discussion


# Study 4: A focus on early childhood (4-5y)

In Study 4, `r nrow(d4_ad_wide)/2` US adults and `r nrow(d4_46_wide)/2` US children between the ages of `r summary(d4_46$age)["Min."] %>% round(2)`-`r summary(d4_46$age)["Max."] %>% round(2)` years (median: `r summary(d4_46$age)["Median"] %>% round(2)`y) each assessed two target characters on 18 mental capacities. To make the study appropriate for children in this age range, this study employed a new set of 18 mental capacities (some but not all of which were used in Studies 1-3). In addition, participants were presented with a more child-friendly visual representation of the 3-point response scale ("no," coded as 0; "kinda," coded as 0.5, "yes," coded as 1). This study employed the "edge case" variant of the general approach, with participants assessing both a beetle or a robot in sequence (with order counterbalanced across participants). (See Chapter II for detailed methods.)

## Special notes on data processing and analysis

## Results

### Adults

### Children (4-5y)

## Discussion


# General discussion of the application or deployment of conceptual representations


# Chapter conclusion









# SCRAPS

## Documenting the application or deployment of conceptual representations through XX

[XX CORRECT TO BE NOT ABOUT FACTOR SCORES! change from factor scores to endorsements. Factor scores don't give a sense of absolutely yes/no.]

Having inferred a conceptual structure for a given group of participants via EFA, I then sought to examine attributions of mental capacities to the particular target characters included in each study within this conceptual structure: To what extent did participants attribute each of the fundamental components of mental life revealed by EFA to a given target character, and how did this attributions vary with age (either within an age group or between age groups)? 

To explore this question, for each study I projected children's data into adults' conceptual space and examined "factor scores"—summaries of each participant's attributions of each of factors revealed by EFA. I used the correlation-preserving "ten Berge" method (as implemented in the "psych" package; Revelle, 2018), imputing missing values using the mean (by target character, capacity, and age group). This yielded one factor score for each of (adults') factors, for each participant. I consider these to be summaries of that person's attributions of the corresponding latent construct.

I analyzed these factor scores via mixed effects Bayesian regression analyses using the "brms" package for R (Bürkner, 2017). In all of these analyses, I included the maximal random effect structures given the design for the relevant study. Further details varied by study, depending on the number of target characters included in that study, the number of factors revealed by EFA for the relevant group(s) of participants, and the goals of the analysis (e.g., comparing two age groups vs. examining continuous effects of age within one or more groups of participants).
