---
title: "Chapter V: Changes in deployment of the concept"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes
   
# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

# Chapter overview

In this chapter, I focus on the third of my three key questions about the development of representations of mental life introduced in Chapter I: _How do people of different ages deploy their conceptual representations of mental life to reason about specific entities in the world?_ As in Chapters III-IV, to address this question I draw on data from all of the current studies (Studies 1-4); for details about the methods of these studies, see Chapter II. The goal of this chapter is to provide "snapshots" of these organizations in early childhood, middle childhood, and adulthood, and to explore in finer-grained detail changes in children's beliefs about the mental lives of animate and inanimate beings between 4-9y of age.



# General analysis plan: Documenting the application or deployment of conceptual representations

3. Tracking which mental capacities are attributed to which beings in the world (Chapter V) provides a way of observing the application or deployment of these conceptual representations in reasoning about specific entities in the real world. For example, if participants who assess the mental capacities of Characters 1, 2, and 3 share one general pattern of mental capacity attributions, and participants who assess the mental capacities of Characters 4, 5, and 6 share another pattern, this provides some evidence that conceptual representations of mental life might play a role in structuring representations of (and interactions with) different classes of beings in the world. 



# Study 1: An adult endpoint

## Special notes on data processing and analysis

## Results

## Discussion


# Study 2: Conceptual change between middle childhood (7-9y) and adulthood

## Special notes on data processing and analysis

## Results

## Discussion


# Study 3: Conceptual change over early and middle childhood (4-9y)

## Special notes on data processing and analysis

## Results

## Discussion


# Study 4: A focus on early childhood (4-5y)

## Special notes on data processing and analysis

## Results

## Discussion


# General discussion of the application or deployment of conceptual representations


# Chapter conclusion









# SCRAPS

## Documenting the application or deployment of conceptual representations through XX

[XX CORRECT TO BE NOT ABOUT FACTOR SCORES! change from factor scores to endorsements. Factor scores don't give a sense of absolutely yes/no.]

Having inferred a conceptual structure for a given group of participants via EFA, I then sought to examine attributions of mental capacities to the particular target characters included in each study within this conceptual structure: To what extent did participants attribute each of the fundamental components of mental life revealed by EFA to a given target character, and how did this attributions vary with age (either within an age group or between age groups)? 

To explore this question, for each study I projected children's data into adults' conceptual space and examined "factor scores"—summaries of each participant's attributions of each of factors revealed by EFA. I used the correlation-preserving "ten Berge" method (as implemented in the "psych" package; Revelle, 2018), imputing missing values using the mean (by target character, capacity, and age group). This yielded one factor score for each of (adults') factors, for each participant. I consider these to be summaries of that person's attributions of the corresponding latent construct.

I analyzed these factor scores via mixed effects Bayesian regression analyses using the "brms" package for R (Bürkner, 2017). In all of these analyses, I included the maximal random effect structures given the design for the relevant study. Further details varied by study, depending on the number of target characters included in that study, the number of factors revealed by EFA for the relevant group(s) of participants, and the goals of the analysis (e.g., comparing two age groups vs. examining continuous effects of age within one or more groups of participants).
