---
title: "Chapter VI: Synthesis and discussion"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes

# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

XX __INTRODUCE DISCUSSION__


# Synthesis: What have we learned about representations of mental life?

## Multiple dimensions of development: Conceptual units, their organization, and their deployment

## "Edge cases" vs. "diverse characters" approaches


# Social consequences

## BODY, HEART, and MIND as "lenses" through which to view a being

## Reasoning about extraordinary beings


# Open questions

## What drives these changes? 

## Development before and after 4-10y

## From conceptual structure to folk theory

## Parallels in other conceptual domains



