---
title: "Chapter VI: Synthesis and discussion"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes

# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

XX __INTRODUCE DISCUSSION__


# Synthesis: What have we learned about representations of mental life?

## Conceptual units, their organization, and their deployment

OUTLINE

- Summary
    - Conceptual units: 
        - Some time during early childhood: HEART differentitation from BODY (& MIND)
        - By middle childhood: robust, adult-like distinctions
    - Organization:
        - From early on: BODY & MIND more basic than HEART
        - Throughout early and into middle childhood: BODY & MIND come to be equally basic (rather than BODY more basic than MIND)
        - Throughout middle childhood (and perhaps beyond): HEART comes to be seen as jointly dependent on BODY + MIND
    - Deployment:
        - From early on: BODY, HEART, & MIND all inform animate-inanimate distinction
        - Through middle childhood (and perhaps beyond): Each comes to play a distinct role: BODY necessary + sufficient, HEART necessary but not sufficient, MIND merely correlated
        - Extending into middle childhood (and perhaps beyond): General tendecies to over-attribute HEART, under-attribute MIND
- Synthesis/speculation
    - Interplay between conceptual units & organization: each informs the other.
        - e.g., hiearchy as a precursor of distinction: for BODY/HEART, some evidence that younger children are treating BODY as more basic than HEART even before they are treating BODY as _distinct_ from HEART
        - e.g., distinction as a precursor of hierarchy: for both BODY/HEART and MIND/HEART, evidence for robust distinctions among older children but hierarchy not nearly as strict as adults
    - Priority of ontology (units/organization) before deployment
        - older children seem very adultlike in units, rather adultlike in organization (but less strict, and no joint dependency), and least adultlike in deployment (quite adultlike, but less strict, in animate-inanimate distinction, but marked over-attribution of HEART, especially to "edge cases")
        - over-attribution of HEART to animates (evident in early childhood and through middle childhood, declines but not to adult levels): A relic of the recent differentiation of HEART from BODY—in combination with a lack of joint dependency on BODY _and_ MIND
        - over-attribution of HEART to inanimates (mostly robot!): A relic of the recent "release" of HEART from MIND? (some intriguing hints that these attributions might actually increase over early childhood (S3))—in combination with a lack of joint dependency on MIND _and_ BODY
        - under-attribution of MIND to both animates and inanimates (becomes more adultlike with age in S2, S3): ?? I don't have a strong intuition on this—might require further study—but it's noteworthy given that MIND is probably the most adult-like unit from early on (but maybe that's because it's the stuff that children _don't_ attribute!). Could children think of this stuff as primarily _human_? (cf. Haslam)


## "Edge cases" vs. "diverse characters" approaches

## Parallels in other conceptual domains


# Social consequences

## BODY, HEART, and MIND as "lenses" through which to view a being

## Lenses, or theories of (motivated) action?

## Reasoning about extraordinary beings


# Open questions

## What drives these changes? 

## Development before and after 4-10y

## From conceptual structure to folk theory




