---
title: "Chapter VI: Synthesis and discussion"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
always_allow_html: yes
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 3, fig.asp = 0.67,
                      include = F, echo = F)
```

```{r}
# # for knitting to .docx
# output:
#   word_document:
#     reference_docx: "./word-styles-reference.docx"
# always_allow_html: yes

# # for knitting to .nb.html 
# output:
#   html_notebook:
#     toc: yes
#     toc_depth: 4
#     toc_float: yes
```

XX __INTRODUCE DISCUSSION__


# Synthesis: What have we learned about representations of mental life?

## Conceptual units, their organization, and their deployment

OUTLINE

- Summary
    - Conceptual units: 
        - Some time during early childhood: HEART differentitation from BODY (& MIND)
        - By middle childhood: robust, adult-like distinctions
    - Organization:
        - From early on: BODY & MIND more basic than HEART
        - Throughout early and into middle childhood: BODY & MIND come to be equally basic (rather than BODY more basic than MIND)
        - Throughout middle childhood (and perhaps beyond): HEART comes to be seen as jointly dependent on BODY + MIND
    - Deployment:
        - From early on: BODY, HEART, & MIND all inform animate-inanimate distinction
        - Through middle childhood (and perhaps beyond): Each comes to play a distinct role: BODY necessary + sufficient, HEART necessary but not sufficient, MIND merely correlated
        - Extending into middle childhood (and perhaps beyond): General tendecies to over-attribute HEART, under-attribute MIND
- Synthesis/speculation
    - Interplay between conceptual units & organization: each informs the other.
        - e.g., hiearchy as a precursor of distinction: for BODY/HEART, some evidence that younger children are treating BODY as more basic than HEART even before they are treating BODY as _distinct_ from HEART
        - e.g., distinction as a precursor of hierarchy: for both BODY/HEART and MIND/HEART, evidence for robust distinctions among older children but hierarchy not nearly as strict as adults
    - Priority of ontology (units/organization) before deployment
        - older children seem very adultlike in units, rather adultlike in organization (but less strict, and no joint dependency), and least adultlike in deployment (quite adultlike, but less strict, in animate-inanimate distinction, but marked over-attribution of HEART, especially to "edge cases")
        - over-attribution of HEART to animates (evident in early childhood and through middle childhood, declines but not to adult levels): A relic of the recent differentiation of HEART from BODY—in combination with a lack of joint dependency on BODY _and_ MIND
        - over-attribution of HEART to inanimates (mostly robot!): A relic of the recent "release" of HEART from MIND? (some intriguing hints that these attributions might actually increase over early childhood (S3))—in combination with a lack of joint dependency on MIND _and_ BODY
        - under-attribution of MIND to both animates and inanimates (becomes more adultlike with age in S2, S3): ?? I don't have a strong intuition on this—might require further study—but it's noteworthy given that MIND is probably the most adult-like unit from early on (but maybe that's because it's the stuff that children _don't_ attribute!). Could children think of this stuff as primarily _human_? (cf. Haslam)


## "Edge cases" vs. "diverse characters" approaches

Across the current studies, I employed two strategies for gauging conceptual representations of mental life through variability in participants' mental capacity attributions: (1) asking participants to assess the mental capacities of two selected "edge cases" in social reasoning, whose mental lives I presumed would elicit different responses across individual participants (a beetle and a robot; Studies 1a-1c, 2, and 4); and (2) asking participants to assess a diverse range of target characters (e.g., humans and a wide variety of other animals, technologies, inert objects), whose mental lives I presumed would be perceived to differ (Study 1d and Study 3). These two "variants" of my experimental approach were introduced in Chapter II; here I discuss the extent to which they provided converging or diverging evidence about conceptual units, their organization, and the deployment of representations of mental life over development.

The two studies with younger children (Study 3, "diverse characters" variant; Study 4, "edge case" variant) varied along so many dimensions—the set of mental capacities included; the physical setup, experimental setting, experimenter's script, and the amount of scaffolding provided for using the response scale; the between- vs. within-subjects design; the average age of participants—that differences between studies cannot reasonably be interpreted as arising from differences in the variant of the experimental approach alone. Given this, I focus my comparisons of these two variants on adults (seven samples: Studies 1a-1d, 2, 3, and 4) and 7- to 9-year-old children (two samples: Study 2 and Study 3).

### Conceptual units

In terms of conceptual units (Chapter III), the "edge case" and "diverse characters" variants appear to have yielded very similar results. 

Among adults, all seven datasets were well accounted for by a three-factor exploratory factor analysis solution featuring conceptual units corresponding to BODY, HEART, and MIND. There was only one adult sample—in Study 2, one of the five studies with adults to employ the "edge case" variant of the approach—for which there was any compelling evidence for a more complex solution (featuring four or more factors), and no adult samples for which there was any indication of a simpler underlying structure (featuring fewer than three factors; see Chapter III, Table 3.1). The BODY, HEART, and MIND factors were qualitatively very similar across adult samples, and accounted for similar proportions of the shared variance in each EFA solution (see Chapter III, Figure 3.5, panel C). 

The two studies with 7- to 9-year-old children (Study 2, "edge case" variant; Study 3, "diverse characters" variant) also converged in their EFA results: Both studies provided strong evidence for a three-factor solution (see Chapter III, Table 3.1), with qualitatively similar BODY, HEART, and MIND factors. The proportion of the shared variance explained by each of these three factors appeared to be more variable across these two studies, among older children, with the HEART factor explaining a disproportionately large amount of variance in mental capacity attributions to the edge cases featured in Study 2, but not to the diverse characters featured in Study 3 (see Chapter III, Figure 3.5, panel C). This is particularly interesting given how dramatically children in this study over-attributed capacities related to the HEART to both of these edge cases, relative to adults (see Chapter VI)—but Studies 2 and 3 also differed substantially in the number of mental capacities included in their design (40 mental capacities in Study 2 vs. 20 mental capacities in Study 3), making it difficult to determine (without further studies) whether the variant of the experimental approach had an impact on the estimated size of conceptual units. In any case, the broad picture of three conceptual units, which correspond closely to the BODY, HEART, and MIND units of adults, was quite similar across these two studies with 7- to 9-year-old children.

In sum, for both adults and 7- to 9-year-old children, the suites of mental capacities that tended to "hang together" when individual participants disagreed in their assessments of the mental lives of "edge cases" were strikingly similar to the suites of mental capacities that tended to "hang together" when target characters were perceived to vary in their mental capacity profiles. Although these two variants of the experimental approach relied to varying degrees on different sources of variability—individual differences in opinion vs. (perceived) differences between target characters—both yielded correlation structures that quite plausibly reflect a common set of latent constructs: the conceptual units that I have called BODY, HEART, and MIND.

### Organization 

In terms of the organization of these conceptual units (Chapter IV), the "edge case" and "diverse characters" approaches appear to have captured the more stable aspects of the relationships between BODY, HEART, and MIND (namely, that BODY and MIND appear to be more "basic" than HEART), while also yielding somewhat different aspects of the finer details of this relational structure (including the nature of the relationship between BODY and MIND, as well as the strength of the correlations among all three conceptual units).

Among adults, the asymmetries in scores on the _BODY_ vs. _HEART_ scales were strikingly consistent across studies (see Chapter IV, Figure 4.10, panel A; and Table 4.11, "BODY-HEART" rows): Virtually all adult participants, in all studies, endorsed BODY abilities at least as strongly as, and often more strongly than, HEART abilities—regardless of which character they assessed (and, by extension, regardless of which variant of the experimental paradigm was employed in that study). The same could be said of the asymmetries in scores on the _MIND_ vs. _HEART_ scales (see Figure 4.10, panel C; and Table 4.11, "HEART-MIND" rows): Virtually all adult participants, in all studies, endorsed MIND abilities at least as strongly as, and often more strongly than, HEART abilities. The MIND vs. HEART asymmetry appears to have been estimated to be slightly smaller in the two adult samples from studies that used the "diverse characters" variant (Study 1d and Study 3) than in the samples from studies that used the "edge cases" variant (Studies 1a-1c, 2, and 4; see Figure 4.10, panel A), but the asymmetry was clearly present in all adult samples. In Chapter IV I took these reliable asymmetries to be evidence that BODY and MIND are more basic, fundamental aspects of mental life, while HEART is more complex and contingent on the presence of BODY and MIND. The "edge case" and "diverse characters" variants of the experimental approach both provided strong evidence for this aspect of the relational structures among conceptual units among adults.

Among 7- to 9-year-old children it also seems to be true that both variants of the experimental approach yielded similar pictures of the relationships between BODY and MIND, on the one hand, and HEART, on the other: The asymmetries between the more "basic" units (BODY and MIND) vs. HEART were generally similar across the two samples of older children, regardless of which variant of the experimental approach was employed (see Chapter IV, Figure 4.10, panels A and C; and Table 4.11, "BODY-HEART" and "HEART-MIND" rows). The only possible exception to this was that in Study 2 ("edge case" variant), the asymmetry in 7- to 9-year-old children's _BODY_ vs. _HEART_ scores appears to have been smaller than the corresponding asymmetry in Study 3 ("diverse characters" variant); indeed, after accounting for other aspects of the experimental design the parameter estimate for this asymmetry was not differentiable from zero (see Figure 4.10, panel B).

Meanwhile, the "edge case" and "diverse characters" variants of the experimental approach yielded much more variable pictures of the relationship between the two more "basic" units—BODY and MIND, both among adults and among 7- to 9-year-old chidlren. 

Among adults, all five of the studies that featured edge cases as target characters suggested that adults tended to endorse MIND more strongly than BODY (albeit not with the same strictness as in the BODY vs. HEART and MIND vs. HEART asymmetries just described); indeed, these studies estimated this asymmetry to be roughly as strong as the asymmetry between BODY vs. HEART (see Chapter IV, Figure 4.10, panel A). The two studies that featured diverse characters, however, appear to have estimated this asymmetry in adults' _BODY_ vs. _MIND_ scores to be much smaller and more variable across target characters, with some target characters eliciting asymmetries in the opposite direction (stronger endorsements of BODY than MIND; see Figure 4.2, panel D; and Figure 4.7, panel A). 

This same pattern holds true among 7- to 9-year-old children (see Chapter IV, Figure 4.10, panel A): In Study 2 ("edge case" variant), children tended to endorse MIND more strongly than BODY on average, while in Study 3 ("diverse characters" variant), there was no systematic asymmetry in children's _BODY_ vs. _MIND_ scores, which reflected the fact that this asymmetry ran in opposite directions for different target characters (see Figure 4.2, panel D).

A final aspect of the relationships among conceptaul units that I explored in Chapter IV was the correlations among scores on _BODY_, _HEART_, and _MIND_ scales. In general, scores on all three scales were positively correlated, as I would expect if all three scales tapped into different aspects of the same more general phenomenon (what I have called "mental life"). However, among both adults and 7- to 9-year-old children, the correlations between BODY vs. MIND appear to have been much stronger in studies that employed the "diverse characters" variant of the approach (Study 1d and Study 3) than in studies that employed the "edge cases" variant (Studies 1a-1c, 2, and 4; (see Chapter IV, Figure 4.10, panel C). A post-hoc visual inspection of Figure 4.1, panel D2, and Figure 4.6, panel A2, suggests that this may be due to the inclusion of more animate than inanimate characters: In both cases, the correlations between BODY vs. MIND appears to have been quite strong among animate characters, and closer to zero among inanimate characters, and the preponderance of animate characters in these studies (17 animates vs. 4 inanimates in Study 1d; 5 animates vs. 4 inanimates in Study 3) may have tipped the balance toward stronger correlations in these cases. Whether these are inflated estimates of the BODY-MIND relationship (because of this imbalance in experimental design), or more accurate estimates (because this imbalance favors the kinds of entities that are the primary targets of reasoning about mental life in the course of most people's ordinary lives) is a difficult judgment to make.

In sum, for both adults and 7- to 9-year-old children, the relationships among BODY and MIND, on the one hand, and HEART, on the other, were generally similar across the two variants of the experimental approach, both in the strength of the positive correlations across conceptual units (if a target was judged to have BODY or MIND abilities, it was more likely to be judged to have HEART abilities) and in the asymmetries between more "basic" vs. less "basic" units (targets were generally judged to have more BODY and MIND abilities than HEART abilities). In contrast, correlations and asymmetries between these two more basic conceptual units, BODY and MIND, appear to have been varied more in their manifestations across the "edge case" vs. "diverse characters" approaches—seemingly because the nature of these relationships seems to have varied across target characters and animacy status. This would not have been clear if I had only conducted studies that employed the "edge case" variant of the experimental approach.

### Deployment

XX OUTLINE

- animate-inanimate distinction
    - BODY: same across variants, for both adults and 7-9yo
    - HEART: seemingly more exaggerated for diverse characters (makes sense! edge cases didn't include anything that adults tend to attribute substantial HEART to)
    - MIND: definitely more exaggerated for diverse characters (also makes sense! edge cases only included things that adults tended to attribute MIND to)
    - again, which is more accurate? in this case, diverse characters - the point of the animate-inaniamte distinction in "deployment" is to capture something about the wide range of entities that people encounter
- beyond the animate-inanimate distinction: over- vs. under-attributions
    - BODY: XX 
    - HEART: XX
    - MIND: XX
    - wrap-up: XX


## Parallels in other conceptual domains


# Social consequences

## BODY, HEART, and MIND as "lenses" through which to view a being

## Lenses, or theories of (motivated) action?

## Reasoning about extraordinary beings


# Open questions

## What drives these changes? 

## Development before and after 4-10y

## From conceptual structure to folk theory




